---
title: 'Modelling Coffee Agroforestry in Central America with CAF2021'
subtitle: 'Progress report III for project SEACAF, sub-contract B0554x4'
author:
- Marcel van Oijen^[Independent researcher, Edinburgh, UK - VanOijenMarcel@gmail.com]
date: '`r Sys.Date()`'
output:
  pdf_document:
    fig_crop: false
    fig_caption: yes
    keep_tex: no
    number_sections: yes
    toc: yes
  word_document:
    reference_docx: word-styles-reference-01.docx
  html_document: default
fontsize: 11pt
geometry: margin=1in
csl: environmental-modelling-and-software.csl
bibliography: [Avocado.bib,Banana.bib,SEACAF.bib]
---

```{r, include=FALSE}
  knitr::opts_chunk$set(echo=F,results="asis",warning=FALSE,message=FALSE)
  library( geosphere )
  library( readxl    )
  library( tidyverse )
```

```{r}
  filesTM <- file.info(list.files(pattern="^BC_Turrialba_Masatepe.*\\.RData$"))
  filesTM <- filesTM[ with(filesTM,order(as.POSIXct(mtime))), ]
  fileTM  <- tail( rownames(filesTM[1]), 1 )
  load( fileTM )
  
  filesTM_MAP <- file.info(list.files(pattern="^CAF2021_parMAP.*\\.rds$"))
  filesTM_MAP <- filesTM_MAP[ with(filesTM_MAP,order(as.POSIXct(mtime))), ]
  fileTM_MAP  <- tail( rownames(filesTM_MAP[1]), 1 )
  # parMAP      <- readRDS( fileTM_MAP )
  parMAP.old  <- readRDS( fileTM_MAP ) ; np.old <- dim(parMAP.old)[1]
  
  # Construct the parMAP (with more parameters than stored in fileTM_MAP)
  source('initialisation/set_CAF2021_Turrialba.R')
  np               <- length( params )
  parMAP           <- matrix( params, nrow=np, ncol=nSites, byrow=F )
  rownames(parMAP) <- names_params
  colnames(parMAP) <- paste0( "s", 1:nSites )
  for(p in 1:np.old) {
    prow          <- which( startsWith( rownames(parMAP),
                                        rownames(parMAP.old)[p] ) )
    for(r in prow) { parMAP[r,] <- parMAP.old[p,] }
  }
```

```{r}
  add.lmleg <- function(orig=FALSE){
    if(orig) { y.lm <- lm( y ~ 0 + x ) }
    else     { y.lm <- lm( y ~ x ) }
    r2   <- round( summary(y.lm)$r.squared, 2 )
    if(orig) {
      abline( 0, y.lm$coefficients[1], col="blue" )
    } else {
      abline( y.lm$coefficients[1], y.lm$coefficients[2], col="blue" )
    }
    legend( "bottomright",
            legend=paste("r2= ",as.character(r2)),
            col=c("blue"), lty=c(1), cex=0.7, bg="transparent" )
  }

  plotxylm <- function(maintxt="Obs. Costa Rica", xtxt="Sim.", orig=FALSE) {
    plot(x,y,xlab=xtxt,ylab="",main=maintxt) ; add.lmleg(orig)
  }
```

```{r}
  load( "df_C.f.rda" )
  load( "df_G.f.rda" )

  n_C.f <- dim(df_C.f)[1] ; n_G.f <- dim(df_G.f)[1]
```



\clearpage

# Correcting errors in df_C.f and df_G.f

## Capping excessive fertilisation rates

```{r}
  iN500_C <- which(df_C.f$Nfert > 500 )
  iN500_G <- which(df_G.f$Nfert > 500 )
  
  cbind( df_C.f$code[iN500_C], df_C.f$Nfert[iN500_C] )
  cbind( df_G.f$code[iN500_G], df_G.f$Nfert[iN500_G] )
  
  df_C.f$Nfert[iN500_C] <- 500
  df_G.f$Nfert[iN500_G] <- 500
```

## Correcting inconsistencies in reported tree and shade variables

```{r}
  if1104 <- which( df_C.f$code==1104 ) # nt=8 but tree densities all 0
  if1157 <- which( df_C.f$code==1157 ) # nt=0 but shade>0 (VisSky<1)
  
  c( df_C.f$nt[if1104], df_C.f$shade[if1104] )
  c( df_C.f$nt[if1157], df_C.f$shade[if1157] )
  
  df_C.f$nt[if1157] <- 1
```



\clearpage

# Pedotransfer functions and updating df_C|G.f

```{r}
  dir.f       <- "data/Farms SEACAF/"
  file_soil.f <- "Soil_general.xlsx"
```

```{r}
  df_soil1.f0 <- read_excel( paste0(dir.f,file_soil.f),
                             sheet="Apparent density", guess_max=3000 )

  df_soil1.f  <- df_soil1.f0 %>%
    mutate( code = ifelse(country=="Costa Rica", 1000,
                   ifelse(country=="Guatemala" , 2000,
                          NA )) ) %>%
    mutate( code = code + farm_number ) %>%
    arrange( code ) %>%
    rename( DM.soil.sample_C     = "weight 105"        ) %>%
    rename( FW.soil.sample_G     = "Fresh weight"      ) %>%
    rename( FW.soil.subsample1_G = "sub sample weight" ) %>%
    rename( AD.soil.subsample1_G = "airdry weight"     ) %>%
    rename( AD.soil.subsample2_G = "Gsubsample_105C"   ) %>%
    rename( DM.soil.subsample2_G = "Gweight_105C"      ) %>%
    mutate( DM.soil.subsample2_G =
              ifelse( DM.soil.subsample2_G < AD.soil.subsample2_G,
                      DM.soil.subsample2_G,
                      AD.soil.subsample2_G ) ) %>%
    mutate( DM.soil.sample =
              ifelse( country=="Costa Rica", DM.soil.sample_C,
              ifelse( country=="Guatemala" , FW.soil.sample_G *
                      (AD.soil.subsample1_G / FW.soil.subsample1_G) *
                      (DM.soil.subsample2_G / AD.soil.subsample2_G),
                      NA )) ) %>%
    group_by( code, Profundity ) %>%
    # summarise( DM.soil.layer = mean(DM.soil.sample,na.rm=T) * 
    summarise( DM.soil.layer = median(DM.soil.sample,na.rm=T) *
                               0.001 * (10000/78.54) ) %>% # kg DM m-2 per layer
    summarise( DM.soil.00_26 = sum(DM.soil.layer) ) %>% # kg DM m-2 in top 26 cm
    mutate( DM.soil = DM.soil.00_26 / (2.6 * 100) ) # DM in kg l-1 in top 26 cm
```

```{r}
  df_soil2.f0 <- read_excel( paste0(dir.f,file_soil.f),
                             sheet="physical_chemical" )

  df_soil2.f <- df_soil2.f0 %>%
    mutate( code = ifelse( startsWith(farm_code,"Costa Rica"), 1000,
                   ifelse( startsWith(farm_code,"Guatemala" ), 2000,
                           NA )) ) %>%
    mutate( code = code + farm_number ) %>%
    arrange( code ) %>%
    rename( Cperc.soil.00_13 = "0-13_%Carbon"    ) %>%
    rename( Cperc.soil.13_26 = "13-26_%Carbon"   ) %>%
    rename( Nperc.soil.00_13 = "0-13_%Nitrogen"  ) %>%
    rename( Nperc.soil.13_26 = "13-26_%Nitrogen" ) %>%
    rename( sand.00_13_C     = "0-13_Sand"       ) %>%
    rename( sand.13_26_C     = "13-26_Sand"      ) %>%
    rename( silt.00_13_C     = "0-13_Silt"       ) %>%
    rename( silt.13_26_C     = "13-26_Silt"      ) %>%
    rename( clay.00_13_C     = "0-13_Clay"       ) %>%
    rename( clay.13_26_C     = "13-26_Clay"      ) %>%
    mutate( sand_C           = 0.5 * (sand.00_13_C + sand.13_26_C) ) %>%
    mutate( silt_C           = 0.5 * (silt.00_13_C + silt.13_26_C) ) %>%
    mutate( clay_C           = 0.5 * (clay.00_13_C + clay.13_26_C) ) %>%
    rename( sand_G           = "General_sand"    ) %>%
    rename( silt_G           = "General_silt"    ) %>%
    rename( clay_G           = "General_clay"    ) %>%
    mutate( sand             = pmax( sand_C, sand_G, na.rm=T )) %>%
    mutate( silt             = pmax( silt_C, silt_G, na.rm=T )) %>%
    mutate( clay             = pmax( clay_C, clay_G, na.rm=T )) %>%
    mutate( Cperc.soil.00_26 = 0.5 * (Cperc.soil.00_13 + Cperc.soil.13_26) ) %>%
    mutate( Nperc.soil.00_26 = 0.5 * (Nperc.soil.00_13 + Nperc.soil.13_26) ) %>%
    mutate( CN.soil          = Cperc.soil.00_26 / Nperc.soil.00_26 ) %>%
    select( code, CN.soil, Cperc.soil.00_26, Nperc.soil.00_26,
            sand, silt, clay )
```

```{r}
  df_soil.f <- df_soil1.f %>%
    inner_join( df_soil2.f, by="code" ) %>%
    mutate( C.soil.00_26 = DM.soil.00_26 * Cperc.soil.00_26 / 100 ) %>%
    mutate( N.soil.00_26 = DM.soil.00_26 * Nperc.soil.00_26 / 100 ) %>%
    mutate( C.soil       = C.soil.00_26  * 1.5 ) %>% # Assuming 2/3 of SM is in top 26 cm
    mutate( N.soil       = N.soil.00_26  * 1.5 ) %>% # Assuming 2/3 of SM is in top 26 cm
    select( code, DM.soil, CN.soil, C.soil, N.soil, sand, silt, clay )
```

```{r}
  # Pedotransfer function derived by Tomasella et al. (2003)
  # as presented and evaluated by Tomasella et al. (2004)
  # We have no data for "Moisture equivalence (Me)" and set it at Me=0.4.
  # Me also add minimum bounds (WP>=0.05, FC>=WP+0.10)
  fTomasella2003 <- function(DM,SI,CL){
    Me  = 0.4
    x14 = -1.05501 + 0.0650857 * SI
    x15 = -2.07588 + 0.0423954 * CL
    x16 = -6.03402 + 4.80572   * DM
    x17 = -2.18409 + 8.84963   * Me
    z9  =  0.175202 + 1.18513 * x17 - 0.0996042 * x17^2 +
           0.327915 * x16 - 0.0758657 * x16^2
    z10 =  0.929344 * z9 + 0.132519 * x14
    z13 =  0.235084 + 0.33033 * x15 - 0.191838 * x15^2 + 0.0543679 * x15^3 +
           0.977685 * x17 + 0.304174 * x15 * x17 - 0.218857 * x17^2 -
           0.164373 * x15 * x17^2 + 0.0415057 * x17^3 +
           0.373361 * x16 + 0.0811861 * x17 * x16 - 0.0768087 * x15 * x17 * x16
    WP  =  pmax( 0.05  , 0.214008 + 0.0862945 * z13 )
    FC  =  pmax( WP+0.1, 0.339255 + 0.112526  * z10 )
    return( list(WP=WP,FC=FC) ) }

    df_water.f <- df_soil.f %>%
      mutate ( WP = fTomasella2003(DM.soil,silt,clay)$WP ) %>%
      mutate ( FC = fTomasella2003(DM.soil,silt,clay)$FC ) %>%
      select ( code, WP, FC ) %>%
      arrange( code )
```

```{r, echo=T}
    summary( df_water.f$WP )
    summary( df_water.f$FC )
    summary( df_water.f$FC - df_water.f$WP )
```

```{r}
  df_water_C.f <- df_water.f %>%
    subset ( df_water.f$code <  2000 ) %>%
    arrange( code )
  df_water_G.f <- df_water.f %>%
    subset ( df_water.f$code >= 2000 ) %>%
    arrange( code )
```

```{r}
  df_C.f <- df_C.f %>%
    inner_join( df_water_C.f, by="code" ) %>%
    arrange   ( code )
  df_G.f <- df_G.f %>%
    inner_join( df_water_G.f, by="code" ) %>%
    arrange   ( code )
  
  n_C.f  <- dim(df_C.f)[1] ; n_G.f <- dim(df_G.f)[1]
```

```{r, eval=F}
# Tropical Andosols (Hodnett & Tomasella 2002)
  VanGenuchten <- function(psi=-1600,a=0.53,n=1.502,thetaR=0.251,thetaS=0.633) {
    theta <- thetaR + (thetaS-thetaR) / (1 + (a*abs(psi))^n)^(1-1/n)
    return( theta ) }

  VanGenuchten( -Inf) # WCAD 0.25
  VanGenuchten(-1600) # WCWP 0.26
  VanGenuchten(  -10) # WCFC 0.41
  VanGenuchten(    0) # WCST 0.63
```



\clearpage

# Weather data 2019-2020 and updating df_C|G.f

```{r}
  dir_weatherstations <- "weather/Climatic_Data/"
    dir_C_Icafe   <- "CostaRica/Icafe/"
    dir_C_IMN     <- "CostaRica/IMN/"
    dir_G_Anacafe <- "Guatemala/Anacafe/"

  dir_Icafe     <- paste0( dir_weatherstations, dir_C_Icafe   ) 
  dir_IMN       <- paste0( dir_weatherstations, dir_C_IMN     )
  dir_Anacafe   <- paste0( dir_weatherstations, dir_G_Anacafe ) 
  
  file_Icafe    <- "Datos confidenciales CLIMA-ICAFE- Convenio CATIE.xlsx"
  files_IMN.TMIN <- list.files( dir_IMN, pattern="*TMIN_TMAX_RAIN.xlsx" )
  files_IMN.TMAX <- list.files( dir_IMN, pattern="*TMIN_TMAX_RAIN.xlsx" )
  files_IMN.RAIN <- list.files( dir_IMN, pattern="*RAIN.xlsx" )
    n_IMN.TMIN   <- length( files_IMN.TMIN )
    n_IMN.TMAX   <- length( files_IMN.TMAX )
    n_IMN.RAIN   <- length( files_IMN.RAIN )
  files_Anacafe <- list.files( dir_Anacafe )
    n_Anacafe   <- length( files_Anacafe )
```

```{r}
  df_Icafe       <- read_excel( paste0(dir_Icafe,file_Icafe) )
  stations_Icafe <- unique(df_Icafe$Estacion) ; n_Icafe <- length(stations_Icafe)

  list_Icafe.a    <- list_Icafe    <- vector( "list", n_Icafe    )
  list_IMN.TMIN.a <- list_IMN.TMIN <- vector( "list", n_IMN.TMIN )
  list_IMN.TMAX.a <- list_IMN.TMAX <- vector( "list", n_IMN.TMAX )
  list_IMN.RAIN.a <- list_IMN.RAIN <- vector( "list", n_IMN.RAIN )
  list_Anacafe.a  <- list_Anacafe  <- vector( "list", n_Anacafe  )

  for( s in 1:n_Icafe ) {
    list_Icafe[[s]]   <- df_Icafe %>% filter( Estacion==stations_Icafe[s] ) }
  for( s in 1:n_IMN.TMIN ) {
    fs <- paste0(dir_IMN,files_IMN.TMIN[s])
    list_IMN.TMIN[[s]] <- read_excel( fs, sheet="TMIN", skip=1,
                                      col_type="numeric" ) }
  for( s in 1:n_IMN.TMAX ) {
    fs <- paste0(dir_IMN,files_IMN.TMAX[s])
    list_IMN.TMAX[[s]] <- read_excel( fs, sheet="TMAX", skip=1,
                                      col_type="numeric" ) }
  for( s in 1:n_IMN.RAIN ) {
    fs <- paste0(dir_IMN,files_IMN.RAIN[s])
    list_IMN.RAIN[[s]] <- read_excel( fs, sheet="RAIN", skip=1,
                                      col_type="numeric" ) }
  for( s in 1:n_Anacafe ) {
    list_Anacafe[[s]] <- read_csv( paste0(dir_Anacafe,files_Anacafe[s]) ) }
```

```{r}
  for( s in 1:n_Icafe ) {
    list_Icafe.a[[s]] <- list_Icafe[[s]] %>%
      rename( ST = Estacion ) %>%
      rename( TMAX    = "Temperatura máxima °C" ) %>%
      rename( TMIN    = "Temperatura mínima °C" ) %>%
      rename( RAIN    = "Lluvia mm" ) %>%
      select( ST, year, month, TMIN, TMAX, RAIN ) %>%
      group_by( ST, year, month ) %>%
      summarize( TMIN = mean(TMIN,na.rm=T),
                 TMAX = mean(TMAX,na.rm=T),
                 RAIN = sum (RAIN,na.rm=T) ) %>%
      group_by ( month ) %>%
      mutate( TMIN.m = mean(TMIN,na.rm=T) ) %>%
      mutate( TMAX.m = mean(TMAX,na.rm=T) ) %>%
      mutate( RAIN.m = mean(RAIN,na.rm=T) ) %>%
      filter( year>=2019 ) %>%
      mutate( TMIN.a = TMIN - TMIN.m ) %>%
      mutate( TMAX.a = TMAX - TMAX.m ) %>%
      mutate( RAIN.a = RAIN - RAIN.m ) %>%
      mutate( lat    = ifelse(ST=="Orosi"      ,  9.78529,
                       ifelse(ST=="Atirro"     ,  9.8612 ,
                       ifelse(ST=="Santa Rosa" ,  9.92852,
                       ifelse(ST=="San Ramón"  , 10.06455,
                       ifelse(ST=="Naranjo"    , 10.10778,
                       ifelse(ST=="Frailes"    ,  9.75   ,
                       ifelse(ST=="San Carlos" ,  9.62661,
                       ifelse(ST=="San Lorenzo",  9.6414 ,
                       ifelse(ST=="Dota"       ,  9.65056,
                              NA ))))))))) ) %>%
      mutate( lon    = ifelse(ST=="Orosi"      , -83.84652,
                       ifelse(ST=="Atirro"     , -83.6358 ,
                       ifelse(ST=="Santa Rosa" , -83.69964,
                       ifelse(ST=="San Ramón"  , -84.47379,
                       ifelse(ST=="Naranjo"    , -84.38361,
                       ifelse(ST=="Frailes"    , -84.05306,
                       ifelse(ST=="San Carlos" , -84.09163,
                       ifelse(ST=="San Lorenzo", -84.02354,
                       ifelse(ST=="Dota"       , -83.9575 ,
                              NA ))))))))) ) %>%
      dplyr::select( ST, lat, lon, year, month, TMIN.a, TMAX.a, RAIN.a )
  }
  # for( s in 1:n_Icafe ) { list_Icafe.a[[s]] %>% print(n = 1) }
```

```{r}
  for(s in 1:n_IMN.TMIN) {
    list_IMN.TMIN.a[[s]] <- list_IMN.TMIN[[s]] %>%
      rename( month = Mes ) %>%
      rename( year = Año ) %>%
      mutate( TMIN = rowMeans( select(.,starts_with("D")), na.rm=T) ) %>%
      dplyr::select( year, month, TMIN ) %>%
      group_by ( month ) %>%
      mutate( TMIN.m = mean(TMIN,na.rm=T) ) %>%
      filter( year>=2019 ) %>%
      mutate( TMIN.a = TMIN - TMIN.m ) %>%
      mutate( ST = substr(files_IMN.TMAX[s],1,5) ) %>%
      dplyr::select( ST, year, month, TMIN.a ) }

  for(s in 1:n_IMN.TMAX) {
    list_IMN.TMAX.a[[s]] <- list_IMN.TMAX[[s]] %>%
      rename( month = Mes ) %>%
      rename( year = Año ) %>%
      mutate( TMAX = rowMeans( select(.,starts_with("D")), na.rm=T) ) %>%
      dplyr::select( year, month, TMAX ) %>%
      group_by ( month ) %>%
      mutate( TMAX.m = mean(TMAX,na.rm=T) ) %>%
      filter( year>=2019 ) %>%
      mutate( TMAX.a = TMAX - TMAX.m ) %>%
      mutate( ST = substr(files_IMN.TMAX[s],1,5) ) %>%
      dplyr::select( ST, year, month, TMAX.a ) }

  for(s in 1:n_IMN.RAIN) {
    list_IMN.RAIN.a[[s]] <- list_IMN.RAIN[[s]] %>%
      rename( month = Mes ) %>%
      rename( year = Año ) %>%
      mutate( RAIN = rowSums( select(.,starts_with("D")), na.rm=T) ) %>%
      dplyr::select( year, month, RAIN ) %>%
      group_by ( month ) %>%
      mutate( RAIN.m = mean(RAIN,na.rm=T) ) %>%
      filter( year>=2019 ) %>%
      mutate( RAIN.a = RAIN - RAIN.m ) %>%
      mutate( ST = substr(files_IMN.RAIN[s],1,5) ) %>%
      dplyr::select( ST, year, month, RAIN.a ) }

  list_IMN.a <- list_IMN.RAIN.a
  for(s in 1:n_IMN.RAIN) {
    list_IMN.a[[s]] <- list_IMN.a[[s]] %>%
      mutate( lat = ifelse(ST==73048,  9.838611,
                    ifelse(ST==73123,  9.852222,
                    ifelse(ST==84187, 10.005   ,
                    ifelse(ST==84189, 10.13733 ,
                    ifelse(ST==88039,  9.766667,
                    ifelse(ST==88047,  9.736667,
                           NA )))))) ) %>%
      mutate( lon = ifelse(ST==73048, -83.90722,
                    ifelse(ST==73123, -83.90861,
                    ifelse(ST==84187, -84.26556,
                    ifelse(ST==84189, -84.1935 ,
                    ifelse(ST==88039, -84.09056,
                    ifelse(ST==88047, -84.00056,
                           NA )))))) ) %>%
      dplyr::select( ST, lat, lon, year, month, RAIN.a )
    }
  for(s in 1:n_IMN.RAIN) {
    sTMIN <- which( files_IMN.RAIN[s] == files_IMN.TMIN )
    if (length(sTMIN>0)) {
      list_IMN.a[[s]] <- list_IMN.a[[s]] %>%
        inner_join( list_IMN.TMIN.a[[sTMIN]], by=c("ST","year","month") ) %>%
        dplyr::select(ST,lat,lon,year,month,TMIN.a,RAIN.a)
    }
    sTMAX <- which( files_IMN.RAIN[s] == files_IMN.TMAX )
    if (length(sTMAX>0)) {
      list_IMN.a[[s]] <- list_IMN.a[[s]] %>%
        inner_join( list_IMN.TMAX.a[[sTMAX]], by=c("ST","year","month") ) %>%
        dplyr::select(ST,lat,lon,year,month,TMIN.a,TMAX.a,RAIN.a)
    }
  }
```

```{r}
  for( s in 1:n_Anacafe ) {
    list_Anacafe.a[[s]] <- list_Anacafe[[s]] %>%
      rename( ST    = ID_ESTACION ) %>%
      rename( lat   = LATITUD     ) %>%
      rename( lon   = LONGITUD    ) %>%
      rename( TMEAN = "TMP" ) %>%
      rename( RAIN  = "RNF" ) %>%
      select( ST, lat, lon, year, month, TMEAN, RAIN ) %>%
      group_by( ST, lat, lon, year, month ) %>%
      summarize( TMEAN = mean(TMEAN,na.rm=T),
                 RAIN  = sum (RAIN ,na.rm=T) ) %>%
      group_by ( month ) %>%
      mutate( TMEAN.m = mean(TMEAN,na.rm=T) ) %>%
      mutate( RAIN.m  = mean(RAIN ,na.rm=T) ) %>%
      filter( year>=2019 ) %>%
      mutate( TMEAN.a = TMEAN - TMEAN.m ) %>%
      mutate( RAIN.a  = RAIN  - RAIN.m  ) %>%
      dplyr::select( ST, lat, lon, year, month, TMEAN.a, RAIN.a )
  }
  # for( s in 1:n_Anacafe ) { list_Anacafe.a[[s]] %>% print(n = 20, width=Inf) }
```

```{r}
  Icafe.a <- list_Icafe.a[[1]]
  for(s in 2:n_Icafe   ) { Icafe.a <- rbind(Icafe.a,list_Icafe.a[[s]]) }
  IMN.a   <- list_IMN.a  [[1]]
  for(s in 2:n_IMN.RAIN) { IMN.a <- rbind( IMN.a, list_IMN.a[[s]] ) }

  C.a     <- rbind( Icafe.a, IMN.a )
  # C.a %>% print(width=Inf,n=Inf)
  
  G.a     <- list_Anacafe.a[[1]]
  for(s in 2:n_Anacafe) { G.a <- rbind( G.a, list_Anacafe.a[[s]] ) }
  ioutlier.TMEAN_G <- which( abs(G.a$TMEAN.a)>5 )
  G.a$TMEAN.a[ioutlier.TMEAN_G] <- NA

  # G.a %>% print(width=Inf,n=Inf)
```

```{r}
  df.ym <- function(df,y,m) {df %>% filter(year==y) %>% filter(month==m)}
```

```{r}
  # Weather stations Costa Rica and their distance from Turrialba
  df=C.a

  lonlat_C.ST <- df[ c("lon","lat") ]
  coordsT     <- c( -83.68,  9.89  ) # Longitude, Latitude
  dist.T      <- as.vector( distm( coordsT, lonlat_C.ST ) ) / 1000
  df          <- df %>% add_column( dist=dist.T )

  par( mfrow=c(3,4), mar=c(2,2,1,1) )

  country="C" ; xvar="dist"
  
  yvar="TMIN.a" ; yrange <- range( df[[yvar]], na.rm=T )
  for(m in 1:12) {
    df.m <- df.ym(df,2019,m) ; x = df.m[[xvar]] ; y = df.m[[yvar]]
    plot( x, y, main=paste0(country,":",yvar," ",m),
          xlab=xvar, ylab="", ylim=yrange )
    abline(h=0,col="black")
    lm <- lm( y ~ x )
    abline( lm$coefficients[1], lm$coefficients[2], col="blue" )
  }
  
  yvar="TMAX.a" ; yrange <- range( df[[yvar]], na.rm=T )
  for(m in 1:12) {
    df.m <- df.ym(df,2019,m) ; x = df.m[[xvar]] ; y = df.m[[yvar]]
    plot( x, y, main=paste0(country,":",yvar," ",m),
          xlab=xvar, ylab="", ylim=yrange )
    abline(h=0,col="black")
    lm <- lm( y ~ x )
    abline( lm$coefficients[1], lm$coefficients[2], col="blue" )
  }
  
  yvar="RAIN.a" ; yrange <- range( df[[yvar]], na.rm=T )
  for(m in 1:12) {
    df.m <- df.ym(df,2019,m) ; x = df.m[[xvar]] ; y = df.m[[yvar]]
    plot( x, y, main=paste0(country,":",yvar," ",m),
          xlab=xvar, ylab="", ylim=yrange )
    abline(h=0,col="black")
    lm <- lm( y ~ x )
    abline( lm$coefficients[1], lm$coefficients[2], col="blue" )
  }
```

```{r}
  # Weather stations Guatemala and their distance from farm 170
  df=G.a

  lonlat_G.ST <- df[ c("lon","lat") ]
  coordsG170  <- c( -90.44, 14.429 ) # Longitude, Latitude
  dist.170    <- as.vector( distm( coordsG170, lonlat_G.ST ) ) / 1000
  df          <- df %>% add_column( dist=dist.170 )

  par( mfrow=c(3,4), mar=c(2,2,1,1) )

  country="G" ; xvar="dist"
  
  yvar="TMEAN.a" ; yrange <- range( df[[yvar]], na.rm=T )
  for(m in 1:12) {
    df.m <- df.ym(df,2019,m) ; x = df.m[[xvar]] ; y = df.m[[yvar]]
    plot( x, y, main=paste0(country,":",yvar," ",m),
          xlab=xvar, ylab="", ylim=yrange )
    abline(h=0,col="black")
    lm <- lm( y ~ x )
    abline( lm$coefficients[1], lm$coefficients[2], col="blue" )
  }
  
  yvar="RAIN.a" ; yrange <- range( df[[yvar]], na.rm=T )
  for(m in 1:12) {
    df.m <- df.ym(df,2019,m) ; x = df.m[[xvar]] ; y = df.m[[yvar]]
    plot( x, y, main=paste0(country,":",yvar," ",m),
          xlab=xvar, ylab="", ylim=yrange )
    abline(h=0,col="black")
    lm <- lm( y ~ x )
    abline( lm$coefficients[1], lm$coefficients[2], col="blue" )
  }
```

```{r}
  C.a.mean2019mon <- C.a %>%
    filter( year == 2019 ) %>%
    group_by( month ) %>%
    summarize( TMIN.a = mean(TMIN.a,na.rm=T),
               TMAX.a = mean(TMAX.a,na.rm=T),
               RAIN.a = mean(RAIN.a,na.rm=T) ) %>%
    as.matrix()
  
  knitr::kable( C.a.mean2019mon )
```

```{r}
  G.a.mean2019mon <- G.a %>%
    filter( year == 2019 ) %>%
    group_by( month ) %>%
    summarize( TMEAN.a = mean(TMEAN.a,na.rm=T),
               RAIN.a  = mean(RAIN.a ,na.rm=T) ) %>%
    as.matrix()
  
  knitr::kable( G.a.mean2019mon )
```

## Extending farm weather files by two years (2019, 2020)

For 2019 we use the country-average monthly anomalies, for 2020 the climatic average.

```{r}
  monl   <- c( 31, 28, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31 )
  monend <- cumsum( monl ) ; monstart <- c( 1, head(monend+1,-1) )
  mon    <- function(doy) { which((doy>=monstart) & (doy<=monend)) }
```

```{r}
  nf <- length( df_C.f$code )

  for(f in 1:nf) {
    w.f                <- df_C.f$weather.WC[[f]]
    ncol               <- dim(w.f)[2]
    meanyear           <- matrix( NA, 365, ncol )
    colnames(meanyear) <- colnames(w.f)
    for(d in 1:365) {
      meanyear[d,] <- colMeans( w.f[ which(w.f[,"doy"]==d), ] )
    }
    anom2019 <- matrix(0,365,ncol) ; colnames(anom2019) <- colnames(w.f)
    for(d in 1:365) {
      anom2019[d,"TMIN"] <- C.a.mean2019mon[ mon(d), "TMIN.a" ]
      anom2019[d,"TMAX"] <- C.a.mean2019mon[ mon(d), "TMAX.a" ]
      anom2019[d,"RAIN"] <- C.a.mean2019mon[ mon(d), "RAIN.a" ] / monl[mon(d)]
    }
    year2020          <- meanyear            ; year2020[,"year"] <- 2020
    year2019          <- meanyear + anom2019 ; year2019[,"year"] <- 2019
    year2019[,"RAIN"] <- pmax( year2019[,"RAIN"], 0 )
    w.f               <- rbind( w.f, year2019, year2020 )
    df_C.f$weather.WC[[f]] <- w.f
    # y20    <- year2020[,"RAIN"] ; y19 <- year2019[,"RAIN"]
    # yrange <- range(y20,y19)
    # plot( y20, main=paste0("RAIN(",f,")"), ylim=yrange, xlab="", ylab="" )
    # points( y19,col="red" )
  }
```

```{r}
  nf <- length( df_G.f$code )

  par( mfrow=c(5,5), mar=c(2,1,1,1) )

  for(f in 1:nf) {
    w.f                <- df_G.f$weather.WC[[f]]
    ncol               <- dim(w.f)[2]
    meanyear           <- matrix( NA, 365, ncol )
    colnames(meanyear) <- colnames(w.f)
    for(d in 1:365) {
      meanyear[d,] <- colMeans( w.f[ which(w.f[,"doy"]==d), ] )
    }
    anom2019 <- matrix(0,365,ncol) ; colnames(anom2019) <- colnames(w.f)
    for(d in 1:365) {
      anom2019[d,"TMIN"] <- G.a.mean2019mon[ mon(d), "TMEAN.a" ]
      anom2019[d,"TMAX"] <- G.a.mean2019mon[ mon(d), "TMEAN.a" ]
      anom2019[d,"RAIN"] <- G.a.mean2019mon[ mon(d), "RAIN.a"  ] / monl[mon(d)]
    }
    year2020          <- meanyear            ; year2020[,"year"] <- 2020
    year2019          <- meanyear + anom2019 ; year2019[,"year"] <- 2019
    year2019[,"RAIN"] <- pmax( year2019[,"RAIN"], 0 )
    w.f               <- rbind( w.f, year2019, year2020 )
    df_G.f$weather.WC[[f]] <- w.f
    # y20    <- year2020[,"TMIN"] ; y19 <- year2019[,"TMIN"]
    # yrange <- range(y20,y19)
    # plot( y20, main=paste0("TMIN(",f,")"), ylim=yrange, xlab="", ylab="" )
    # points( y19,col="red" )
  }
```



\clearpage

# Yields from second harvest season (2019-2020) and updating df_C|G.f

```{r}
  dir.f            <- "data/Farms SEACAF/"
  file_yield1920.f <- "Database SEACAF - Net income.xlsx"
```

```{r}
  df_yield1920.f <- read_excel( paste0(dir.f,file_yield1920.f) )

  df_yield1920.f <- df_yield1920.f %>%
    mutate ( code      = ifelse(country=="Costa Rica", 1000,
                         ifelse(country=="Guatemala" , 2000,
                                NA )) ) %>%
    mutate ( code_farm = as.numeric( substring(code_farm,first=3) ) ) %>%
    mutate ( code      = code + code_farm ) %>%
    arrange( code ) %>%
    mutate ( yield1920 = prodcafe_ha / 3 ) %>%
    dplyr::select( code, yield1920 )
```

```{r}
  df_yield1920_C.f <- df_yield1920.f %>%
    subset ( df_yield1920.f$code <  2000 ) %>%
    arrange( code )
  df_yield1920_G.f <- df_yield1920.f %>%
    subset( df_yield1920.f$code >= 2000 ) %>%
    arrange( code )
```

```{r}
  lonlat_C.f  <- df_C.f[ c("lon","lat") ]
  lonlat_G.f  <- df_G.f[ c("lon","lat") ]
  coords.T    <- c( -83.68,  9.89  ) # Longitude, Latitude
  coords.2170 <- c( -90.44, 14.429 ) # Longitude, Latitude
  dist_C.T    <- as.vector( distm( coords.T   , lonlat_C.f ) ) / 1000
  dist_G.2170 <- as.vector( distm( coords.2170, lonlat_G.f ) ) / 1000
```

```{r}
  df_C.f <- df_C.f %>%
    rename( yield1819=yield ) %>%
    inner_join( df_yield1920_C.f, by=c("code") ) %>%
    mutate( dist=dist_C.T ) %>%
    dplyr::select( code, lat, lon, dist, slope, altitude, alt.WC, weather.WC,
                   DM.soil, CN.soil, C.soil, N.soil, Nfert, WP, FC,
                   nt, shade, yield1819, yield1920 ) %>%
    arrange( code )
    
  df_G.f <- df_G.f %>%
    rename( yield1819=yield ) %>%
    inner_join( df_yield1920_G.f, by=c("code") ) %>%
    mutate( dist=dist_G.2170) %>%
    dplyr::select( code, lat, lon, dist, slope, altitude, alt.WC, weather.WC,
                   DM.soil, CN.soil, C.soil, N.soil, Nfert, WP, FC,
                   nt, shade, yield1819, yield1920 ) %>%
    arrange( code )
  
  n_C.f <- dim(df_C.f)[1] ; n_G.f <- dim(df_G.f)[1]
```

```{r}
  par( mfrow=c(2,2), mar=c(2,2,3,2) )

  x = df_C.f$yield1819 ; y = df_C.f$yield1920
  plotxylm( "Yields 19/20 vs. 18/19\nCosta Rica", ""  )

  x = df_G.f$yield1819 ; y = df_G.f$yield1920
  plotxylm( "Yields 19/20 vs. 18/19\nGuatemala", ""  )

  x = df_C.f$dist      ; y = df_C.f$yield1920 - df_C.f$yield1819
  ynna <- which(!is.na(y))
  x <- x[ynna] ; y <- y[ynna]
  plotxylm( "Yield-change vs. dist. Turrialba", ""  )

  x = df_G.f$dist      ; y = df_G.f$yield1920 - df_G.f$yield1819
  ynna <- which(!is.na(y))
  x <- x[ynna] ; y <- y[ynna]
  plotxylm( "Yield-change vs. dist. G170", ""  )
```



\clearpage

# Data on tree densities and updating df_C|G.f

```{r}
  dir.f        <- "data/Farms SEACAF/"
  file_trees.f <- "Copy of class_marcel JH.xlsx"
```

```{r}
  df_trees.f <- read_excel( paste0(dir.f,file_trees.f) )

  df_trees.f <- df_trees.f %>%
    mutate ( code = ifelse(cod_country=="Costa Rica", 1000,
                    ifelse(cod_country=="Guatemala" , 2000,
                           NA )) ) %>%
    mutate ( code = code + num_farm    ) %>%
    arrange( code ) %>%
    mutate ( dens_Erythrina = Erythina2     ) %>%
    mutate ( dens_Inga      = Legume2       ) %>%
    mutate ( dens_Avocado   = Fruit2        ) %>%
    mutate ( dens_Banana    = Musacea2      ) %>%
    mutate ( dens_Grevillea = `non-Legume2` ) %>%
    mutate ( dens_Cordia    = Timber2       ) %>%
    mutate ( dens_timber    = dens_Grevillea + dens_Cordia ) %>%
    mutate ( dens_Grevillea = ifelse(dens_Grevillea>dens_Cordia,dens_timber,0) ) %>%
    mutate ( dens_Cordia    = ifelse(dens_Grevillea>dens_Cordia,0,dens_timber) ) %>%
    dplyr::select( code, dens_Erythrina, dens_Inga,
                         dens_Avocado  , dens_Banana,
                         dens_Grevillea, dens_Cordia )
  # df_trees.f %>% print( n=Inf, width=Inf)
```

```{r}
  df_trees_C.f <- df_trees.f %>%
    subset ( df_trees.f$code <  2000 ) %>%
    arrange( code )
  df_trees_G.f <- df_trees.f %>%
    subset ( df_trees.f$code >= 2000 ) %>%
    arrange( code )
```

```{r}
  df_C.f <- df_C.f %>%
    inner_join( df_trees_C.f, by=c("code") ) %>%
    dplyr::select( code, lat, lon, dist, slope, altitude, alt.WC, weather.WC,
                   DM.soil, CN.soil, C.soil, N.soil, Nfert, WP, FC, nt, shade,
                   dens_Erythrina, dens_Inga, dens_Avocado, dens_Banana,
                   dens_Grevillea, dens_Cordia, yield1819, yield1920 ) %>%
    arrange( code )
    
  df_G.f <- df_G.f %>%
    inner_join( df_trees_G.f, by=c("code") ) %>%
    dplyr::select( code, lat, lon, dist, slope, altitude, alt.WC, weather.WC,
                   DM.soil, CN.soil, C.soil, N.soil, Nfert, WP, FC, nt, shade,
                   dens_Erythrina, dens_Inga, dens_Avocado, dens_Banana,
                   dens_Grevillea, dens_Cordia, yield1819, yield1920 ) %>%
    arrange( code )
  
  n_C.f <- dim(df_C.f)[1] ; n_G.f <- dim(df_G.f)[1]
```

```{r}
  par( mfrow=c(2,3), mar=c(4,2,3,2) )

  y1a_C = df_C.f$dens_Erythrina ; y1b_C = df_C.f$dens_Inga
  y1a_G = df_G.f$dens_Erythrina ; y1b_G = df_G.f$dens_Inga
  ymax1 = max( y1a_C, y1b_C, y1a_G, y1b_G )
  
  y2a_C = df_C.f$dens_Avocado   ; y2b_C = df_C.f$dens_Banana
  y2a_G = df_G.f$dens_Avocado   ; y2b_G = df_G.f$dens_Banana
  ymax2 = max( y2a_C, y2b_C, y2a_G, y2b_G )
  
  y3a_C = df_C.f$dens_Grevillea ; y3b_C = df_C.f$dens_Cordia
  y3a_G = df_G.f$dens_Grevillea ; y3b_G = df_G.f$dens_Cordia
  ymax3 = max( y3a_C, y3b_C, y3a_G, y3b_G )
  
  plot  ( y1a_C, main="Costa Rica trees [1]",
          xlab="farm index", ylab="", ylim=c(0,1.25*ymax1))
  points( y1b_C, col="red" )
  legend( "top",legend=c("Erythrina","Inga"),
          horiz=T, pch=1, col=c("black","red"), bg="transparent" )

  plot  ( y2a_C, main="Costa Rica trees [2]",
          xlab="farm index", ylab="", ylim=c(0,1.25*ymax2))
  points( y2b_C, col="red" )
  legend( "top",legend=c("Avocado","Banana"),
          horiz=T, pch=1, col=c("black","red"), bg="transparent" )

  plot  ( y3a_C, main="Costa Rica trees [3]",
          xlab="farm index", ylab="", ylim=c(0,1.25*ymax3))
  points( y3b_C, col="red" )
  legend( "top",legend=c("Grevillea","Cordia"),
          horiz=T, pch=1, col=c("black","red"), bg="transparent" )

  plot  ( y1a_G, main="Guatemala trees [1]",
          xlab="farm index", ylab="", ylim=c(0,1.25*ymax1))
  points( y1b_G, col="red" )
  legend( "top",legend=c("Erythrina","Inga"),
          horiz=T, pch=1, col=c("black","red"), bg="transparent" )

  plot  ( y2a_G, main="Guatemala trees [2]",
          xlab="farm index", ylab="", ylim=c(0,1.25*ymax2))
  points( y2b_G, col="red" )
  legend( "top",legend=c("Avocado","Banana"),
          horiz=T, pch=1, col=c("black","red"), bg="transparent" )

  plot  ( y3a_G, main="Guatemala trees [3]",
          xlab="farm index", ylab="", ylim=c(0,1.25*ymax3))
  points( y3b_G, col="red" )
  legend( "top",legend=c("Grevillea","Cordia"),
          horiz=T, pch=1, col=c("black","red"), bg="transparent" )
```



\clearpage

# Trees

## Tree management

```{r}
  namesdfscalars <- names(df_C.f)[ !(names(df_C.f) %in% "weather.WC") ]
  
  df_C.f$dens_service <- df_C.f$dens_Erythrina  + df_C.f$dens_Inga
  df_C.f$dens_fruit   <- df_C.f$dens_Banana     + df_C.f$dens_Avocado
  df_C.f$dens_timber  <- df_C.f$dens_Grevillea  + df_C.f$dens_Cordia
  i.s <- which( df_C.f$dens_service >
               max( df_C.f$dens_Erythrina , df_C.f$dens_Inga ) )
  i.f <- which( df_C.f$dens_fruit   >
               max( df_C.f$dens_Banana    , df_C.f$dens_Avocado ) )
  i.t <- which( df_C.f$dens_service >
                max( df_C.f$dens_Grevillea, df_C.f$dens_Cordia ) )
  df_C.f[i.s,namesdfscalars]
  
  df_G.f$dens_service <- df_G.f$dens_Erythrina  + df_G.f$dens_Inga
  df_G.f$dens_fruit   <- df_G.f$dens_Banana     + df_G.f$dens_Avocado
  df_G.f$dens_timber  <- df_G.f$dens_Grevillea  + df_G.f$dens_Cordia
  i.s <- which( df_G.f$dens_service >
               max( df_G.f$dens_Erythrina , df_G.f$dens_Inga ) )
  i.f <- which( df_G.f$dens_fruit   >
               max( df_G.f$dens_Banana    , df_G.f$dens_Avocado ) )
  i.t <- which( df_G.f$dens_service >
                max( df_G.f$dens_Grevillea, df_G.f$dens_Cordia ) )
```

### Erythrina
- Pruning, no thinning
- Prescribed pruning intensity of 90% twice a year (at coffee flowering and pre-harvest). Say doy 140 and 350.
- Pruned material always stays on site

### Inga
- Pruning, no thinning
- Pruning once a year (at flowering or just before). Say doy 140.
- Pruning intensity for shade-target
- Pruned branches stay on site in CRI but are removed in GTM

### Avocado
- Pruning, no thinning
- Prescribed pruning intensity ?

### Banana
- No pruning or thinning
- Annual senescence modelled through TC-parameters
- Dead material always stays on site

### Grevillea
- Pruning, no thinning
- Pruning once a year (at flowering or just before). Say doy 140.
- Pruning intensity for shade-target
- Pruned branches stay on site in CRI but are removed in GTM

### Cordia
- Thinning, no pruning. Say once every five years.
- Thinning intensity for shade-target
- Thinned trunks always removed
- Branches from thinned trees stay on site in CRI but are removed in GTM !!


## Tree allometry & other parameters

### Erythrina
- Calibration Turrialba
- N-fixing

### Inga
- Calibration Masatepe
- Edwin's report, Table 8 on p. 19
- N-fixing

### Avocado
- My progress report

### Banana
- My progress report

### Grevillea
- Edwin's report, Table 10 on p. 21

### Cordia
- My report of ~2007



\clearpage

# Simulating farms in Costa Rica and Guatemala

We run the model for each of the farm locations in Costa Rica and Guatemala, using a variety of parameterisations.

```{r}
  outputSummary <- function( output ) {
    idoy           <- which( outputNames=="doy" )
    names_vars     <- c(
      "harvDM_f_hay", "harvCPT_f", "harvCPT_2"  , "harvCST_f", "harvCST_3",
      "D_Nsoil"     , "D_Csoil"  , "D_C"        , "D_CT"     , "D_Csys"   ,
      "Shade_f"     , "NfixT_f"  , "Nleaching_f", "Crunoff_f",
      "Csoil_f"     , "harvDM_f_ha1819", "harvDM_f_ha1920" )
    
    fOut           <- matrix( NA, nrow=1, ncol=length(names_vars) )
    colnames(fOut) <- names_vars

    iyear      <- which( outputNames=="year" )
    idoy       <- which( outputNames=="doy" )
    
    ih_f_hay   <- which( outputNames=="harvDM_f_hay" ) # kg C ha-1 y-1
    ihCPT_f    <- which( outputNames=="harvCPT_f"    ) # kg C m-2 d-1
    ihCPT_2    <- which( outputNames=="harvCPT_t(2)" ) # kg C m-2 d-1
    ihCST_f    <- which( outputNames=="harvCST_f"    ) # kg C m-2 d-1
    ihCST_3    <- which( outputNames=="harvCST_t(3)" ) # kg C m-2 d-1
    iNsoil_f   <- which( outputNames=="Nsoil_f"      ) # kg N m-2
    iCsoil_f   <- which( outputNames=="Csoil_f"      ) # kg C m-2 
    iC_f       <- which( outputNames=="C_f"          ) # kg C m-2
    iCT_f      <- which( outputNames=="CT_f"         ) # kg C m-2
    
    iShade_f   <- which( outputNames=="Shade_f"      ) # m2 m-2
    
    iNfixT     <- which( outputNames=="NfixT_f"      ) # kg N m-2 d-1
    iNleaching <- which( outputNames=="Nleaching_f"  ) # kg N m-2 d-1
    iCrunoff   <- which( outputNames=="Crunoff_f"    ) # kg C m-2 d-1
    
    idayH1     <- which( outputNames=="DayHarv(1)" )
    idayH2     <- which( outputNames=="DayHarv(2)" )

    c.DM  <- 1 / 0.47          # 'kg C' -> 'kg DM'
    NDAYS <- dim(output)[1]
    c.hay <- 1e4 * 365 / NDAYS # 'm-2 in sim. period' -> 'ha-1 y-1'
    d181  <- which( output[,idoy]==181 )
    
    fOut[,"harvDM_f_hay"] <- mean( output[d181,ih_f_hay] )
    fOut[,"harvCPT_f"   ] <- sum ( output[    ,ihCPT_f ] ) * c.DM * c.hay
    fOut[,"harvCPT_2"   ] <- sum ( output[    ,ihCPT_2 ] ) * c.DM * c.hay
    fOut[,"harvCST_f"   ] <- sum ( output[    ,ihCST_f ] ) * c.DM * c.hay
    fOut[,"harvCST_3"   ] <- sum ( output[    ,ihCST_3 ] ) * c.DM * c.hay
    
    D_output         <- output[NDAYS,] - output[1,]
    fOut[,"D_Nsoil"] <- D_output[iNsoil_f] * c.hay
    fOut[,"D_Csoil"] <- D_output[iCsoil_f] * c.hay
    fOut[,"D_C"    ] <- D_output[iC_f    ] * c.hay
    fOut[,"D_CT"   ] <- D_output[iCT_f   ] * c.hay
    fOut[,"D_Csys" ] <- fOut[,"D_Csoil"] + fOut[,"D_C"] + fOut[,"D_CT"]

    fOut[,"Shade_f"    ] <- mean( output[,iShade_f  ] )
    
    outputFinalYearMean  <- colMeans( output[ (NDAYS-364):NDAYS, ] )
    fOut[,"NfixT_f"    ] <- outputFinalYearMean[iNfixT    ] * 1e4 * 365
    fOut[,"Nleaching_f"] <- outputFinalYearMean[iNleaching] * 1e4 * 365
    fOut[,"Crunoff_f"  ] <- outputFinalYearMean[iCrunoff  ] * 1e4 * 365
    
    fOut[,"Csoil_f"    ] <- output[1,iCsoil_f]

    dHarv1819 <- which( (output[,iyear]==2019) & (output[,idoy]==181) )
    dHarv1920 <- which( (output[,iyear]==2020) & (output[,idoy]==181) )
    fOut[,"harvDM_f_ha1819"] <- output[dHarv1819,ih_f_hay]
    fOut[,"harvDM_f_ha1920"] <- output[dHarv1920,ih_f_hay]

    return( fOut )
  }
```

```{r}
  varnames <- c(
    "harvDM_f_hay", "harvCPT_f", "harvCPT_2"  , "harvCST_f", "harvCST_3",
    "D_Nsoil"     , "D_Csoil"  , "D_C"        , "D_CT"     , "D_Csys"   ,
    "Shade_f"     , "NfixT_f"  , "Nleaching_f", "Crunoff_f",
    "Csoil_f"     , "harvDM_f_ha1819", "harvDM_f_ha1920" )

  ip_CNLITT0     <- which( names_params=="CNLITT0"     )
  ip_CNSOMF0     <- which( names_params=="CNSOMF0"     )
  ip_CNSOMS0     <- which( names_params=="CNSOMS0"     )
  ip_CSOM0       <- which( names_params=="CSOM0"       )
  ip_LAT         <- which( names_params=="LAT"         )
  ip_SHADETARGET <- which( names_params=="SHADETARGET" )
  ip_SLOPE       <- which( names_params=="SLOPE"       )
  
  ip_FWCAD  <- which( names_params=="FWCAD"  )
  ip_FWCFC  <- which( names_params=="FWCFC"  )
  ip_FWCWET <- which( names_params=="FWCWET" )
  ip_FWCWP  <- which( names_params=="FWCWP"  )
  ip_WCST   <- which( names_params== "WCST"  )
  
  ip_FHARVBT1 <- which( names_params== "FHARVBT(1)" )
  ip_FHARVBT2 <- which( names_params== "FHARVBT(2)" )
  ip_FHARVBT3 <- which( names_params== "FHARVBT(3)" )
  ip_FHARVLT1 <- which( names_params== "FHARVLT(1)" )
  ip_FHARVLT2 <- which( names_params== "FHARVLT(2)" )
  ip_FHARVLT3 <- which( names_params== "FHARVLT(3)" )
  
  ip_PRUNTARGET1 <- which( names_params== "PRUNTARGET(1)" )
  ip_PRUNTARGET2 <- which( names_params== "PRUNTARGET(2)" )
  ip_PRUNTARGET3 <- which( names_params== "PRUNTARGET(3)" )
  ip_THINTARGET1 <- which( names_params== "THINTARGET(1)" )
  ip_THINTARGET2 <- which( names_params== "THINTARGET(2)" )
  ip_THINTARGET3 <- which( names_params== "THINTARGET(3)" )
```

```{r list_outF_C}
  list_outF_C     <- vector( "list", n_C.f )
  for(fi in 1:n_C.f) {
    C_C     <- df_C.f$C.soil [ fi ]
    CN_C    <- df_C.f$CN.soil[ fi ]
    LAT_C   <- df_C.f$lat    [ fi ]
    SLOPE_C <- df_C.f$slope  [ fi ]
    Nfert_C <- df_C.f$Nfert  [ fi ]
    shade_C <- df_C.f$shade  [ fi ]
    
    WCWP_C  <- df_C.f$WP[ fi ]
    WCFC_C  <- df_C.f$FC[ fi ]
    WCAD_C  <- 0.01
    WCST_C  <- min( 1, WCFC_C+0.1 )
    WCWET_C <- 0.5 * (WCFC_C + WCST_C)
    
    densE_C <- df_C.f$dens_Erythrina[ fi ]
    densI_C <- df_C.f$dens_Inga     [ fi ]
    densB_C <- df_C.f$dens_Banana   [ fi ]
    densA_C <- df_C.f$dens_Avocado  [ fi ]
    densG_C <- df_C.f$dens_Grevillea[ fi ]
    densC_C <- df_C.f$dens_Cordia   [ fi ]
    
    source( sitesettings_filenames[1] )
    NDAYS_fi          <- as.integer(15*365)
    year_start_fi     <- as.integer(2005)
    doy_start_fi      <- as.integer( 214)
    matrix_weather_fi <- read_listweather_CAF( list_w = df_C.f$weather.WC,
                                               f      = fi,
                                               y1     = year_start_fi,
                                               d1     = doy_start_fi,
                                               nd     = NDAYS_fi )

    calendar_fert_fi <- matrix( -1, nrow=100, ncol=3 )
    calendar_fert_fi [ 1:57, 1 ] <- rep( 2002:2020, each=3 )
    calendar_fert_fi [ 1:57, 2 ] <- c( 135, 289, 350 )
    calendar_fert_fi [ 1:57, 3 ] <- rep( Nfert_C/3, 3 )

    nF_C                     <- 2
    mat_outF                 <- matrix( NA, nF_C, 1+length(varnames) )
    colnames( mat_outF )     <- c( "FarmSetting", varnames )
    mat_outF[,"FarmSetting"] <- 1:nF_C
    
    # source(sitesettings_filenames[31])
    calendar_prunT_fi <- set_prunT( densE_C, densI_C, densB_C, densA_C,
                                    densG_C, densC_C )
    calendar_thinT_fi <- set_thinT( densE_C, densI_C, densB_C, densA_C,
                                    densG_C, densC_C )
    
    for(iF in 1:nF_C) {
      if ( iF==1 ) {
        params_fi <- parMAP[,31]
      } else if ( iF==2 ) {
        params_fi <- parMAP[,11]
      } else {
        stop(paste("Farm setting",iF,"not specified."))
      }
      params_fi <- set_parT( "C", densE_C, densI_C, densB_C,
                                  densA_C, densG_C, densC_C, p.old=params_fi )
      params_fi[ c(ip_CNLITT0,ip_CNSOMF0,ip_CNSOMS0) ] <- CN_C
      params_fi[ ip_CSOM0                            ] <- C_C
      params_fi[ ip_LAT                              ] <- LAT_C
      params_fi[ ip_SLOPE                            ] <- SLOPE_C
      params_fi[ ip_SHADETARGET                      ] <- shade_C
      params_fi[ ip_FWCAD  ] <- WCAD_C  / WCST_C
      params_fi[ ip_FWCWP  ] <- WCWP_C  / WCST_C
      params_fi[ ip_FWCFC  ] <- WCFC_C  / WCST_C
      params_fi[ ip_FWCWET ] <- WCWET_C / WCST_C
      params_fi[ ip_WCST   ] <- WCST_C
      params_fi[ ip_PRUNTARGET1 ] <- 1
      params_fi[ ip_PRUNTARGET2 ] <- 1
      params_fi[ ip_PRUNTARGET3 ] <- 1
      params_fi[ ip_THINTARGET1 ] <- 0
      params_fi[ ip_THINTARGET2 ] <- 0
      params_fi[ ip_THINTARGET3 ] <- 0
      # if( iF>1 ) { } # Include other farm settings here
      outF <- run_model( params_fi, matrix_weather_fi, calendar_fert_fi,
        calendar_prunC, calendar_prunT_fi, calendar_thinT_fi, NDAYS_fi )
      mat_outF[iF,1+(1:length(varnames))] <- outputSummary( outF )
    }
    list_outF_C[[fi]] <- mat_outF
  }
```

```{r list_outF_G}
  list_outF_G     <- vector( "list", n_G.f )
  for(fi in 1:n_G.f) {
    C_G     <- df_G.f$C.soil [ fi ]
    CN_G    <- df_G.f$CN.soil[ fi ]
    LAT_G   <- df_G.f$lat    [ fi ]
    SLOPE_G <- df_G.f$slope  [ fi ]
    Nfert_G <- df_G.f$Nfert  [ fi ]
    shade_G <- df_G.f$shade  [ fi ]
    
    WCWP_G  <- df_G.f$WP[ fi ]
    WCFC_G  <- df_G.f$FC[ fi ]
    WCAD_G  <- 0.01
    WCST_G  <- min( 1, WCFC_G+0.1 )
    WCWET_G <- 0.5 * (WCFC_G + WCST_G)
    
    densE_G <- df_G.f$dens_Erythrina[ fi ]
    densI_G <- df_G.f$dens_Inga     [ fi ]
    densB_G <- df_G.f$dens_Banana   [ fi ]
    densA_G <- df_G.f$dens_Avocado  [ fi ]
    densG_G <- df_G.f$dens_Grevillea[ fi ]
    densC_G <- df_G.f$dens_Cordia   [ fi ]
    
    source( sitesettings_filenames[1] )
    NDAYS_fi          <- as.integer(15*365)
    year_start_fi     <- as.integer(2005)
    doy_start_fi      <- as.integer( 214)
    matrix_weather_fi <- read_listweather_CAF( list_w = df_G.f$weather.WC,
                                               f      = fi,
                                               y1     = year_start_fi,
                                               d1     = doy_start_fi,
                                               nd     = NDAYS_fi )

    calendar_fert_fi <- matrix( -1, nrow=100, ncol=3 )
    calendar_fert_fi [ 1:57, 1 ] <- rep( 2002:2020, each=3 )
    calendar_fert_fi [ 1:57, 2 ] <- c( 135, 289, 350 )
    calendar_fert_fi [ 1:57, 3 ] <- rep( Nfert_G/3, 3 )

    nF_G                     <- 2
    mat_outF                 <- matrix( NA, nF_G, 1+length(varnames) )
    colnames( mat_outF )     <- c( "FarmSetting", varnames )
    mat_outF[,"FarmSetting"] <- 1:nF_G
    
    # source(sitesettings_filenames[31])
    calendar_prunT_fi <- set_prunT( densE_G, densI_G, densB_G, densA_G,
                                    densG_G, densC_G )
    calendar_thinT_fi <- set_thinT( densE_G, densI_G, densB_G, densA_G,
                                    densG_G, densC_G )

    for(iF in 1:nF_G) {
      if ( iF==1 ) {
        params_fi <- parMAP[,31]
      } else if ( iF==2 ) {
        params_fi <- parMAP[,11]
      } else {
        stop(paste("Farm setting",iF,"not specified."))
      }
      params_fi <- set_parT( "G", densE_G, densI_G, densB_G,
                                  densA_G, densG_G, densC_G, p.old=params_fi )
      params_fi[ c(ip_CNLITT0,ip_CNSOMF0,ip_CNSOMS0) ] <- CN_G
      params_fi[ ip_CSOM0                            ] <- C_G
      params_fi[ ip_LAT                              ] <- LAT_G
      params_fi[ ip_SLOPE                            ] <- SLOPE_G
      params_fi[ ip_SHADETARGET                      ] <- shade_G
      params_fi[ ip_FWCAD  ] <- WCAD_G  / WCST_G
      params_fi[ ip_FWCWP  ] <- WCWP_G  / WCST_G
      params_fi[ ip_FWCFC  ] <- WCFC_G  / WCST_G
      params_fi[ ip_FWCWET ] <- WCWET_G / WCST_G
      params_fi[ ip_WCST   ] <- WCST_G
      params_fi[ ip_PRUNTARGET1 ] <- 1
      params_fi[ ip_PRUNTARGET2 ] <- 1
      params_fi[ ip_PRUNTARGET3 ] <- 1
      params_fi[ ip_THINTARGET1 ] <- 0
      params_fi[ ip_THINTARGET2 ] <- 0
      params_fi[ ip_THINTARGET3 ] <- 0
      # if( iF>1 ) { } # Include other farm settings here
      outF <- run_model( params_fi, matrix_weather_fi, calendar_fert_fi,
        calendar_prunC, calendar_prunT_fi, calendar_thinT_fi, NDAYS_fi )
      mat_outF[iF,1+(1:length(varnames))] <- outputSummary( outF )
    }
    list_outF_G[[fi]] <- mat_outF
  }
```


```{r df_CG.f_sim}
  df_C.f_sim <- df_C.f %>%
    select ( code ) %>%
    arrange( code ) %>%
    mutate ( outF  = list_outF_C )

  df_G.f_sim <- df_G.f %>%
    select ( code ) %>%
    arrange( code ) %>%
    mutate ( outF  = list_outF_G )
```

## Summary results

```{r}
  dfoutFSummary <- function( df=df_C.f_sim, Fi=1 ){
    nf     <- dim( df )[1]
    vnames <- colnames( df$outF[[1]] ) ; nv <- length(vnames)
    matres <- matrix( NA, nf, nv ) ; colnames( matres) <- vnames
    F.v    <- matres
    for(fi in 1:nf){
      F.v[fi,] <- df$outF[[fi]][Fi,]
    }
    return( F.v )
  }
```

```{r}
  F1_C             <- dfoutFSummary( df_C.f_sim, Fi=1 )
  F1_G             <- dfoutFSummary( df_G.f_sim, Fi=1 )
  
  Csoil_F1_C.f_sim <- F1_C[,"Csoil_f"]
  Shade_F1_C.f_sim <- F1_C[,"Shade_f"]
  yF1_C.f_sim      <- F1_C[,"harvDM_f_hay"   ]
  yF1_C.f_sim1819  <- F1_C[,"harvDM_f_ha1819"]
  yF1_C.f_sim1920  <- F1_C[,"harvDM_f_ha1920"]

  Csoil_F1_G.f_sim <- F1_G[,"Csoil_f"]
  Shade_F1_G.f_sim <- F1_G[,"Shade_f"]
  yF1_G.f_sim      <- F1_G[,"harvDM_f_hay"   ]
  yF1_G.f_sim1819  <- F1_G[,"harvDM_f_ha1819"]
  yF1_G.f_sim1920  <- F1_G[,"harvDM_f_ha1920"]
```

```{r}
  F2_C             <- dfoutFSummary( df_C.f_sim, Fi=2 )
  F2_G             <- dfoutFSummary( df_G.f_sim, Fi=2 )
  
  Csoil_F2_C.f_sim <- F2_C[,"Csoil_f"]
  Shade_F2_C.f_sim <- F2_C[,"Shade_f"]
  yF2_C.f_sim      <- F2_C[,"harvDM_f_hay"   ]
  yF2_C.f_sim1819  <- F2_C[,"harvDM_f_ha1819"]
  yF2_C.f_sim1920  <- F2_C[,"harvDM_f_ha1920"]

  Csoil_F2_G.f_sim <- F2_G[,"Csoil_f"]
  Shade_F2_G.f_sim <- F2_G[,"Shade_f"]
  yF2_G.f_sim      <- F2_G[,"harvDM_f_hay"   ]
  yF2_G.f_sim1819  <- F2_G[,"harvDM_f_ha1819"]
  yF2_G.f_sim1920  <- F2_G[,"harvDM_f_ha1920"]
```

```{r}
  par( mfrow=c(2,2), mar=c(3,3,1,1) )

  plot( df_C.f$C.soil, Csoil_F1_C.f_sim )
  plot( df_G.f$C.soil, Csoil_F1_G.f_sim )
  plot( df_C.f$shade , Shade_F1_C.f_sim )
  plot( df_G.f$shade , Shade_F1_G.f_sim )
```

```{r}
  par( mfrow=c(2,2), mar=c(3,3,1,1) )

  plot( df_C.f$C.soil, Csoil_F2_C.f_sim )
  plot( df_G.f$C.soil, Csoil_F2_G.f_sim )
  plot( df_C.f$shade , Shade_F2_C.f_sim )
  plot( df_G.f$shade , Shade_F2_G.f_sim )
```

Fig. \ref{fig:XX13} shows that, in the simulations, yields in 2018-19 and 2019-20 were slightly below the long-term average for many farms in Costa Rica, but above-average in Guatemala.

```{r XX13, fig.height=4, fig.cap="\\label{fig:XX13}Simulated yields in 2018-19 and 2019-20 vs. long-term average yields in the same simulations."}
  par( mfrow=c(1,2), mar=c(3,3,2,2) )

  plot( yF1_C.f_sim, yF1_C.f_sim1819, main="Costa Rica (sim.)",
        xlab="mean yield", ylab="kg DM ha-1 y-1")
  points( yF1_C.f_sim, yF1_C.f_sim1920, col="red" )
  abline(1,1,lty=2)
  legend( "bottomright",legend=c("y=x","18/19","19/20"),
          lty=c(2,NA,NA), pch=c(NA,1,1), col=c("black","black","red"),
          bg="transparent" )
  
  plot( yF1_G.f_sim, yF1_G.f_sim1819, main="Guatemala (sim.)",
        xlab="mean yield", ylab="yield 2018/19")
  points( yF1_G.f_sim, yF1_G.f_sim1920, col="red" )
  abline(1,1,lty=2)
  legend( "bottomright",legend=c("y=x","18/19","19/20"),
          lty=c(2,NA,NA), pch=c(NA,1,1), col=c("black","black","red"),
          bg="transparent" )
```

We now finally come to the simulations for all farms that were intended to be more realistic, by using farm-specific information on weather, soil, nitrogen fertilisation rate, and number of shade tree species. In the absence of detailed information on shade tree species and shade management, we made the following assumptions:

- If the number of reported shade tree species was 1, we simulated a system shaded by Inga laurina (managed as in Masatepe experiment treatment 31)
- If there were 2 species, we added Simarouba glauca (conform Masatepe experiment treatment 31)
- If there were 3 or more species, we added banana.

Results of these simulations are shown in Figs \ref{fig:XX14}, \ref{fig:XX15}, and \ref{fig:XX16}. Fig. \ref{fig:XX14} shows how the long-term average annual coffee yields simulated by the model for the years 2000-2014 compares to the yield reported for the farms for the year 2019. The correlations are not very strong. Fig. \ref{fig:XX15} shows, for farms in Costa Rica, observations and simulations of multiple variables, all plotted against each farm's N-fertilisation rate. Farms are grouped by number of shade tree species but no clear differences between the groups are visible. Apart from shade, all variables show a positive or negative correlation with fertilisation. The negative correlation in the case of soil carbon loss in runoff is likely due to fertilisation enhancing vegetation LAI, which in the model reduces erosion. The same variables are shown in Fig. \ref{fig:XX16} for Guatemala, with similar results albeit more difficult to see because of the distorting influence of having farms with excessive N-fertilisation rate in the plots.

```{r XX14, fig.height=4, fig.cap="\\label{fig:XX14}Observed vs. simulated yields in 2018-19 and 2019-20 at the farms in Costa Rica (left) and Guatemala (right)."}
  par( mfrow=c(2,2), mar=c(4,2,2,2), mgp=c(2,1,0) )

  x=yF1_C.f_sim1819 ; y=df_C.f$yield1819
    plotxylm("Yields Costa Rica 18/19", orig=F)
  x=yF1_G.f_sim1819 ; y=df_G.f$yield1819
    plotxylm("Yields Guatemala 18/19" , orig=F)

  x=yF1_C.f_sim1920 ; y=df_C.f$yield1920
    plotxylm("Yields Costa Rica 19/20", orig=F)
  x=yF1_G.f_sim1920 ; y=df_G.f$yield1920
    plotxylm("Yields Guatemala 19/20" , orig=F)
```

```{r XX14b, fig.height=4, fig.cap="\\label{fig:XX14b}Observed vs. simulated yields in 2018-19 and 2019-20 at the farms in Costa Rica (left) and Guatemala (right). Farm setting 2."}
  par( mfrow=c(2,2), mar=c(4,2,2,2), mgp=c(2,1,0) )

  x=yF2_C.f_sim1819 ; y=df_C.f$yield1819
    plotxylm("Yields Costa Rica 18/19", orig=F)
  x=yF2_G.f_sim1819 ; y=df_G.f$yield1819
    plotxylm("Yields Guatemala 18/19" , orig=F)

  x=yF2_C.f_sim1920 ; y=df_C.f$yield1920
    plotxylm("Yields Costa Rica 19/20", orig=F)
  x=yF2_G.f_sim1920 ; y=df_G.f$yield1920
    plotxylm("Yields Guatemala 19/20" , orig=F)
```

```{r}
  int1_C <- which(df_C.f$nt <2) ; int1_G <- which(df_G.f$nt <2)
  int2_C <- which(df_C.f$nt==2) ; int2_G <- which(df_G.f$nt==2)
  int3_C <- which(df_C.f$nt >2) ; int3_G <- which(df_G.f$nt >2)
  
  nnt1_C <- length(int1_C)      ; nnt1_G <- length(int1_G)
  nnt2_C <- length(int2_C)      ; nnt2_G <- length(int2_G)
  nnt3_C <- length(int3_C)      ; nnt3_G <- length(int3_G)
  
  listmat_nt_C <- listmat_nt_G <- vector( "list", 3 )
  varnames.listmat <- c( "code","slope","Nfert","nt","shade",
    "y1819","y1920",  "y1819.sim","y1920.sim","y.sim",
    "D_Csoil.sim","shade.sim","Nleach.sim","Crunoff.sim","Csoil.sim" )
```

```{r}
  listmat_nt_C[[1]] <- t( sapply( 1:nnt1_C, function(i){ cbind(
    df_C.f    [int1_C,]$code     [[i]],
    df_C.f    [int1_C,]$slope    [[i]],
    df_C.f    [int1_C,]$Nfert    [[i]],
    df_C.f    [int1_C,]$nt       [[i]],
    df_C.f    [int1_C,]$shade    [[i]],
    df_C.f    [int1_C,]$yield1819[[i]],
    df_C.f    [int1_C,]$yield1920[[i]],
    df_C.f_sim[int1_C,]$outF     [[i]][,"harvDM_f_ha1819"][1],
    df_C.f_sim[int1_C,]$outF     [[i]][,"harvDM_f_ha1920"][1],
    df_C.f_sim[int1_C,]$outF     [[i]][,"harvDM_f_hay"   ][1],
    df_C.f_sim[int1_C,]$outF     [[i]][,"D_Csoil"        ][1],
    df_C.f_sim[int1_C,]$outF     [[i]][,"Shade_f"        ][1],
    df_C.f_sim[int1_C,]$outF     [[i]][,"Nleaching_f"    ][1],
    df_C.f_sim[int1_C,]$outF     [[i]][,"Crunoff_f"      ][1],
    df_C.f_sim[int1_C,]$outF     [[i]][,"Csoil_f"        ][1]
  ) } ) )
  colnames(listmat_nt_C[[1]]) <- varnames.listmat

  listmat_nt_C[[2]] <- t( sapply( 1:nnt2_C, function(i){ cbind(
    df_C.f    [int2_C,]$code     [[i]],
    df_C.f    [int2_C,]$slope    [[i]],
    df_C.f    [int2_C,]$Nfert    [[i]],
    df_C.f    [int2_C,]$nt       [[i]],
    df_C.f    [int2_C,]$shade    [[i]],
    df_C.f    [int2_C,]$yield1819[[i]],
    df_C.f    [int2_C,]$yield1920[[i]],
    df_C.f_sim[int2_C,]$outF     [[i]][,"harvDM_f_ha1819"][1],
    df_C.f_sim[int2_C,]$outF     [[i]][,"harvDM_f_ha1920"][1],
    df_C.f_sim[int2_C,]$outF     [[i]][,"harvDM_f_hay"   ][1],
    df_C.f_sim[int2_C,]$outF     [[i]][,"D_Csoil"        ][1],
    df_C.f_sim[int2_C,]$outF     [[i]][,"Shade_f"        ][1],
    df_C.f_sim[int2_C,]$outF     [[i]][,"Nleaching_f"    ][1],
    df_C.f_sim[int2_C,]$outF     [[i]][,"Crunoff_f"      ][1],
    df_C.f_sim[int2_C,]$outF     [[i]][,"Csoil_f"        ][1]
  ) } ) )
  colnames(listmat_nt_C[[2]]) <- varnames.listmat

  listmat_nt_C[[3]] <- t( sapply( 1:nnt3_C, function(i){ cbind(
    df_C.f    [int3_C,]$code     [[i]],
    df_C.f    [int3_C,]$slope    [[i]],
    df_C.f    [int3_C,]$Nfert    [[i]],
    df_C.f    [int3_C,]$nt       [[i]],
    df_C.f    [int3_C,]$shade    [[i]],
    df_C.f    [int3_C,]$yield1819[[i]],
    df_C.f    [int3_C,]$yield1920[[i]],
    df_C.f_sim[int3_C,]$outF     [[i]][,"harvDM_f_ha1819"][1],
    df_C.f_sim[int3_C,]$outF     [[i]][,"harvDM_f_ha1920"][1],
    df_C.f_sim[int3_C,]$outF     [[i]][,"harvDM_f_hay"   ][1],
    df_C.f_sim[int3_C,]$outF     [[i]][,"D_Csoil"        ][1],
    df_C.f_sim[int3_C,]$outF     [[i]][,"Shade_f"        ][1],
    df_C.f_sim[int3_C,]$outF     [[i]][,"Nleaching_f"    ][1],
    df_C.f_sim[int3_C,]$outF     [[i]][,"Crunoff_f"      ][1],
    df_C.f_sim[int3_C,]$outF     [[i]][,"Csoil_f"        ][1]
  ) } ) )
  colnames(listmat_nt_C[[3]]) <- varnames.listmat
```

```{r}
  listmat_nt_G[[1]] <- t( sapply( 1:nnt1_G, function(i){ cbind(
    df_G.f    [int1_G,]$code     [[i]],
    df_G.f    [int1_G,]$slope    [[i]],
    df_G.f    [int1_G,]$Nfert    [[i]],
    df_G.f    [int1_G,]$nt       [[i]],
    df_G.f    [int1_G,]$shade    [[i]],
    df_G.f    [int1_G,]$yield1819[[i]],
    df_G.f    [int1_G,]$yield1920[[i]],
    df_G.f_sim[int1_G,]$outF     [[i]][,"harvDM_f_ha1819"][1],
    df_G.f_sim[int1_G,]$outF     [[i]][,"harvDM_f_ha1920"][1],
    df_G.f_sim[int1_G,]$outF     [[i]][,"harvDM_f_hay"   ][1],
    df_G.f_sim[int1_G,]$outF     [[i]][,"D_Csoil"        ][1],
    df_G.f_sim[int1_G,]$outF     [[i]][,"Shade_f"        ][1],
    df_G.f_sim[int1_G,]$outF     [[i]][,"Nleaching_f"    ][1],
    df_G.f_sim[int1_G,]$outF     [[i]][,"Crunoff_f"      ][1],
    df_G.f_sim[int1_G,]$outF     [[i]][,"Csoil_f"        ][1]
  ) } ) )
  colnames(listmat_nt_G[[1]]) <- varnames.listmat

  listmat_nt_G[[2]] <- t( sapply( 1:nnt2_G, function(i){ cbind(
    df_G.f    [int2_G,]$code     [[i]],
    df_G.f    [int2_G,]$slope    [[i]],
    df_G.f    [int2_G,]$Nfert    [[i]],
    df_G.f    [int2_G,]$nt       [[i]],
    df_G.f    [int2_G,]$shade    [[i]],
    df_G.f    [int2_G,]$yield1819[[i]],
    df_G.f    [int2_G,]$yield1920[[i]],
    df_G.f_sim[int2_G,]$outF     [[i]][,"harvDM_f_ha1819"][1],
    df_G.f_sim[int2_G,]$outF     [[i]][,"harvDM_f_ha1920"][1],
    df_G.f_sim[int2_G,]$outF     [[i]][,"harvDM_f_hay"   ][1],
    df_G.f_sim[int2_G,]$outF     [[i]][,"D_Csoil"        ][1],
    df_G.f_sim[int2_G,]$outF     [[i]][,"Shade_f"        ][1],
    df_G.f_sim[int2_G,]$outF     [[i]][,"Nleaching_f"    ][1],
    df_G.f_sim[int2_G,]$outF     [[i]][,"Crunoff_f"      ][1],
    df_G.f_sim[int2_G,]$outF     [[i]][,"Csoil_f"        ][1]
  ) } ) )
  colnames(listmat_nt_G[[2]]) <- varnames.listmat

  listmat_nt_G[[3]] <- t( sapply( 1:nnt3_G, function(i){ cbind(
    df_G.f    [int3_G,]$code     [[i]],
    df_G.f    [int3_G,]$slope    [[i]],
    df_G.f    [int3_G,]$Nfert    [[i]],
    df_G.f    [int3_G,]$nt       [[i]],
    df_G.f    [int3_G,]$shade    [[i]],
    df_G.f    [int3_G,]$yield1819[[i]],
    df_G.f    [int3_G,]$yield1920[[i]],
    df_G.f_sim[int3_G,]$outF     [[i]][,"harvDM_f_ha1819"][1],
    df_G.f_sim[int3_G,]$outF     [[i]][,"harvDM_f_ha1920"][1],
    df_G.f_sim[int3_G,]$outF     [[i]][,"harvDM_f_hay"   ][1],
    df_G.f_sim[int3_G,]$outF     [[i]][,"D_Csoil"        ][1],
    df_G.f_sim[int3_G,]$outF     [[i]][,"Shade_f"        ][1],
    df_G.f_sim[int3_G,]$outF     [[i]][,"Nleaching_f"    ][1],
    df_G.f_sim[int3_G,]$outF     [[i]][,"Crunoff_f"      ][1],
    df_G.f_sim[int3_G,]$outF     [[i]][,"Csoil_f"        ][1]
  ) } ) )
  colnames(listmat_nt_G[[3]]) <- varnames.listmat
```

```{r}
  plotimpacts_nt.Nfert <- function( listmat=listmat_nt_C, var="y.sim" ){
    plot  ( listmat[[1]][,"Nfert"], listmat[[1]][,var],
      xlab="Nfert", ylab="",main=var, pch=1,
      xlim=c(0,max(listmat[[1]][,"Nfert"],listmat[[2]][,"Nfert"],
                   listmat[[3]][,"Nfert"])),
      ylim=c(min(0,listmat[[1]][,var],listmat[[2]][,var],listmat[[3]][,var],
                 na.rm=T),
             max(  listmat[[1]][,var],listmat[[2]][,var],listmat[[3]][,var],
                 na.rm=T)) )
    points( listmat[[2]][,"Nfert"], listmat[[2]][,var], pch=20, col="red"  )
    points( listmat[[3]][,"Nfert"], listmat[[3]][,var], pch=6, col="blue" )
    
    y.lm.nt1 <- lm( listmat[[1]][,var] ~ listmat[[1]][,"Nfert"] )
    y.lm.nt2 <- lm( listmat[[2]][,var] ~ listmat[[2]][,"Nfert"] )
    y.lm.nt3 <- lm( listmat[[3]][,var] ~ listmat[[3]][,"Nfert"] )
    r2.nt1   <- round( summary(y.lm.nt1)$r.squared, 2 )
    r2.nt2   <- round( summary(y.lm.nt2)$r.squared, 2 )
    r2.nt3   <- round( summary(y.lm.nt3)$r.squared, 2 )
    abline( y.lm.nt1$coefficients[1], y.lm.nt1$coefficients[2], col="black" )
    abline( y.lm.nt2$coefficients[1], y.lm.nt2$coefficients[2], col="red" )
    abline( y.lm.nt3$coefficients[1], y.lm.nt3$coefficients[2], col="blue" )
    legend( "bottomright", title="r2",
            legend=c( paste("n<2:",as.character(r2.nt1)),
              paste("n=2:",as.character(r2.nt2)),
              paste("n>2:",as.character(r2.nt3)) ),
            col=c("black","red","blue"), lty=c(1), cex=0.5 )
  }
```

```{r XX15, fig.height=7.5, fig.cap="\\label{fig:XX15}Observations of shade and yield for farms in Costa Rica plus simulations of seven variables: Long-term average coffee yield, Yield in 2018-19, Change in soil carbon, Average shade level, Final year nitrogen leaching, Final year carbon loss in run-off, Soil carbon."}
  par(mfrow=c(3,3),mar=c(4,2,2,2), mgp=c(2,1,0))

  plotimpacts_nt.Nfert( listmat_nt_C, "shade"       )
  plotimpacts_nt.Nfert( listmat_nt_C, "y1819"       )
  plotimpacts_nt.Nfert( listmat_nt_C, "y1920"       )
  plotimpacts_nt.Nfert( listmat_nt_C, "shade.sim"   )
  plotimpacts_nt.Nfert( listmat_nt_C, "y1819.sim"   )
  plotimpacts_nt.Nfert( listmat_nt_C, "y1920.sim"   )
  plotimpacts_nt.Nfert( listmat_nt_C, "D_Csoil.sim" )
  plotimpacts_nt.Nfert( listmat_nt_C, "Nleach.sim"  )
  plotimpacts_nt.Nfert( listmat_nt_C, "Crunoff.sim" )
```

```{r XX16, fig.height=7.5, fig.cap="\\label{fig:XX16}Shade- and yield-observations for farms in Guatemala plus simulations of seven variables: see previous figure for explanation of variables."}
  par(mfrow=c(3,3),mar=c(4,2,2,2), mgp=c(2,1,0))

  plotimpacts_nt.Nfert( listmat_nt_G, "shade"       )
  plotimpacts_nt.Nfert( listmat_nt_G, "y1819"       )
  plotimpacts_nt.Nfert( listmat_nt_G, "y1920"       )
  plotimpacts_nt.Nfert( listmat_nt_G, "shade.sim"   )
  plotimpacts_nt.Nfert( listmat_nt_G, "y1819.sim"   )
  plotimpacts_nt.Nfert( listmat_nt_G, "y1920.sim"   )
  plotimpacts_nt.Nfert( listmat_nt_G, "D_Csoil.sim" )
  plotimpacts_nt.Nfert( listmat_nt_G, "Nleach.sim"  )
  plotimpacts_nt.Nfert( listmat_nt_G, "Crunoff.sim" )
```
