---
title: 'Modelling Coffee Agroforestry in Central America with CAF2021'
subtitle: 'Progress report II for project SEACAF, sub-contract B0554x4'
author:
- Marcel van Oijen^[Independent researcher, Edinburgh, UK - VanOijenMarcel@gmail.com]
date: '`r Sys.Date()`'
output:
  pdf_document:
    fig_crop: false
    fig_caption: yes
    keep_tex: no
    number_sections: yes
    toc: yes
  word_document:
    reference_docx: word-styles-reference-01.docx
  html_document: default
fontsize: 11pt
geometry: margin=1in
csl: environmental-modelling-and-software.csl
bibliography: [Avocado.bib,Banana.bib,MvO.bib]
---

```{r, include=FALSE}
  knitr::opts_chunk$set(echo=F,results="asis",warning=FALSE,message=FALSE)
```

```{r, include=FALSE}
  filesTM <- file.info(list.files(pattern="^BC_Turrialba_Masatepe.*\\.RData$"))
  # filesT  <- file.info(list.files(pattern="^BC_Turrialba......\\.RData$"))
  # filesM  <- file.info(list.files(pattern="^BC_Masatepe.*\\.RData$"))
  filesTM <- filesTM[with(filesTM, order(as.POSIXct(mtime))), ]
  fileTM  <- tail( rownames(filesTM[1]), 1 )
```

# AGENDA 1: Improving the Masatepe-BC May-June 2021

- Tree data
  - Careful: Thinned trees are typically not representative of the stand.
  - When data are in FWT, perhaps assume that 25% of tree woody *volume* is water (Cermak et al. 2007). We would then still need wood density (kg DM m-3) to be able to convert from FWT to DM.
  - Tree biomass reported for ABG only or whole-tree including roots?
  - Ignore 'Biomasa  de rebrotes a 3 metros de inga 2009.xls': extremely light pruning, providing no measure of branch biomass etc. Better data in 'Biomasa arboles  primer raleo por especie A S 2008.xls' which was an intensive pollarding (perhaps 90% of branch pruned), so those data provide a better estimate of the amount of leaves and branches on an Inga tree.
- Data Martin Noponen
- Fertilisation timing
  - CI & CM 2 applications: 15 June, 15 Sep
  - OI & OM 1 application: 30 April (end of dry season)
- Include TCSOM parameters and aim for near-balance of sources and sinks?
- When there are two timber species they will not overlap much, perhaps each could reach 60% of ground cover.
- Inga is not a shade-plant like coffee and will suffer if fully overshadowed by timber trees. But coffee production would then suffer as well. Good management therefore aims to keep timber tree shade below 60%. 

# AGENDA 2: Redoing the Turrialba-BC June 2021 (experiment and fruit trees)

- Use latest model version
- Use all data:
  - Martin Noponen: soil, GHG balance, etc.
  - Roland Cerda: banana & citrus
    - From Rolando's file: choose farms with high fruit tree density and simulate them as extra treatments in the Turrialba experiment (for soil, weather etc.): EMu = poro + banana, ECi = poro + citrus.
  - Fertilisation timings as in file Oriana or as in Masatepe?
  - Assumptions about non-leaching at zero-fertilisation
  - Better weather data for final years?
- Include TCSOM parameters and aim for near-balance of sources and sinks?

# AGENDA 3: BC Llano Bonito (and perhaps Aquiares)

- Files from Oriana. LB at 1600+ m, Aquiares at 1000+ m.
- At LB there were Musaceae, but not in the data files (two tree species could then not be handled by CAF2014), but maybe check the paper by Louise Meylan that is referred to in Oriana et al's 2020 paper.
- Aquiares had unusual poro management: no thinning, no pruning.

# Turrialba and Masatepe

## Parameter settings

- Compared to Masatepe, we set soil carbon time constants (TCLITT, TCSOMF, TCSOMS) for Turrialba at lower values and have a larger fraction of SOM in the fast pool (larger FCSOMF0).
- RNLEACH	is set at 0.5 for both sites. However, the fraction of N that leaches depends on soil type (Harmand et al. 2007), so different settings for the two sites would be realistic.
  - Our notes give values of leaching in Turrialba of 16-27 kgN ha-1 y-1. Where do these numbers come from (which publication, which experimental treatments)?

## Calibration data and constraints

- Csoil: we should expect the sites in Masatepe to be closer to equilibrium from the start than the Turrialba ones because of differences in preceding land-use. The experiment in Masatepe followed on earlier use for coffee production (so no land-use change) whereas the site in Turrialba was originally used for sugar cane. Also, the volcanic soils in Masatepe tend to be bind organic matter and minerals better than the soils at Turrialba. These differences in soil properties may explain why Noponen found greater Csoil-loss in Turrialba despite lower initial Csoil-stock there.
- Other biogeochemistry balances to include?
- Leaching of N: expected to be very small in case of lowest fertilisation.
- Consider recalculating the coffee yields in Nicaragua by dividing FWT by 3.87 (rather than the current value of 3), which would make all yields 22.5% lower.

- Aboveground tree biomass in 2016 (Mg C ha-1) for Masatepe was taken from Sepulveda et al. (2016), Table 12, and units were converted to kg C m-2.
  - NOT USEABLE: 2016 is beyond simulation period.

```{r}
  Sepulveda_treatments <- c(
    "ILSG_CM", "ILSG_OI",
    "SGTR_CI", "SGTR_CM", "SGTR_OI", "SGTR_OM",
    "SSIL_CI", "SSIL_CM", "SSIL_OI", "SSIL_OM",
    "SSTR_CM", "SSTR_OI")
  Sepulveda_CabgT_f       <- c(
     40.1    ,  32.6    ,
     61.1    ,  60.5    ,  56.4    ,  55.6    ,
     19.6    ,  21.7    ,  24.7    ,  19.9    ,
     51.1    ,  51.2    ) * 1e3 * 1e-4
  cbind( Sepulveda_treatments, Sepulveda_CabgT_f )
```

Carbon pools for Costa Rica in 2009 were taken from Noponen (2012, thesis Table A4.1) and converted from Mg C ha-1 to kg C m-2. 

```{r}
Noponen_treatments <- c(
  "C_CM" , "C_OI" ,
  "E_CI" , "E_CM" , "E_OI", "E_OM",
  "ET_CM", "ET_OI",
  "FS_CI", "FS_CM",
  "T_CI" , "T_CM" , "T_OI", "T_OM" )
Noponen_CabgT_f    <- round( c(
   87.57 ,  87.62 ,
    9.69 ,  18.79 ,  16.96,  16.64,
   41.82 ,  23.98 ,
    0    ,   0    ,
   81.82 ,  41.21 ,  38.65,  36.39 ) * 1e3 * 1e-4, 2 )
Noponen_Cabg_f     <- round( c(
    4.05 ,   4.35 ,
    5.16 ,   4.54 ,   5.55,   5.58,
    4.50 ,   3.82 ,
    4.98 ,   3.41 ,
    5.41 ,   4.19 ,   4.36,   1.51 ) * 1e3 * 1e-4, 2 )
cbind( Noponen_treatments, Noponen_CabgT_f, Noponen_Cabg_f )
```

Changes during the nine years 2001-2010 in  soil carbon pools for both countries were given by Noponen (2012, thesis Tables A5.2, A5.3). The values given in those tables were main effects for the shade and fertilisation treatments which we added to estimate carbon change in each of the experimental treatments. The Noponen data are in Mg C ha-1 for the top 40 cm of soil (which we assumed contained 75% of total soil carbon). We thus converted the data to kg C m-2 y-1 in the full soil column by multiplying with 1000 * (100/75) / 9.

The calculations were:

```{r}
        DSOC_CRI_shade  <- c(  -9.23, -13.86, -5.89, -12.54, -7.26 )
  names(DSOC_CRI_shade) <- c( "FS"  , "E"   , "ET" , "C"   , "T"   )
        DSOC_CRI_fert   <- c( -11.40, -10.94, -7.49, -10.44 )
  names(DSOC_CRI_fert)  <- c( "CI"  , "CM"  , "OI" , "OM"   )

        DSOC_NIC_shade  <- c( -2.97,  0    , -3.97 , -2.37,   14.20 )
  names(DSOC_NIC_shade) <- c( "FS" , "ILSG", "ILSS", "SGTR", "SSTR" )
        DSOC_NIC_fert   <- c( -6.08,  1.07 ,  2.12 ,  0.82 )
  names(DSOC_NIC_fert)  <- c( "CI" , "CM"  , "OI"  , "OM"  )
  
  n_CRI_shade <- c( 2, 4, 2, 2, 4 )
  n_CRI_fert  <- c( 3, 5, 4, 2 )
  n_NIC_shade <- c( 2, 2, 4, 4, 2 )
  n_NIC_fert  <- c( 3, 5, 4, 2  )
  
  mCRI <- 0.5 * (
    sum( DSOC_CRI_shade * n_CRI_shade ) / sum(n_CRI_shade) +
    sum( DSOC_CRI_fert  * n_CRI_fert  ) / sum(n_CRI_fert ) )
    
  mNIC <- 0.5 * (
    sum( DSOC_NIC_shade * n_NIC_shade ) / sum(n_NIC_shade) +
    sum( DSOC_NIC_fert  * n_NIC_fert  ) / sum(n_NIC_fert ) )
  
  aCRI_shade <- DSOC_CRI_shade - mCRI
  aCRI_fert  <- DSOC_CRI_fert  - mCRI
  aNIC_shade <- DSOC_NIC_shade - mNIC
  aNIC_fert  <- DSOC_NIC_fert  - mNIC
  
  treatments_CRI <- c(
    "Tu01_E_AC.R" , "Tu02_E_MC.R" , "Tu03_E_MO.R" , "Tu04_E_BO.R" ,
    "Tu05_T_AC.R" , "Tu06_T_MC.R" , "Tu07_T_MO.R" , "Tu08_T_BO.R" ,
    "Tu09_C_MC.R" , "Tu10_C_MO.R" ,
    "Tu13_TE_MC.R", "Tu14_TE_MO.R",
    "Tu19_PS_AC.R", "Tu20_PS_MC.R" )
  effects_CRI    <- mCRI + c(
    aCRI_shade["E" ] + aCRI_fert["CI"],
    aCRI_shade["E" ] + aCRI_fert["CM"],
    aCRI_shade["E" ] + aCRI_fert["OI"],
    aCRI_shade["E" ] + aCRI_fert["OM"],
    aCRI_shade["T" ] + aCRI_fert["CI"],
    aCRI_shade["T" ] + aCRI_fert["CM"],
    aCRI_shade["T" ] + aCRI_fert["OI"],
    aCRI_shade["T" ] + aCRI_fert["OM"],
    aCRI_shade["C" ] + aCRI_fert["CM"],
    aCRI_shade["C" ] + aCRI_fert["OI"],
    aCRI_shade["ET"] + aCRI_fert["CM"],
    aCRI_shade["ET"] + aCRI_fert["OI"],
    aCRI_shade["FS"] + aCRI_fert["CI"],
    aCRI_shade["FS"] + aCRI_fert["CM"] ) # kgC ha-1 in top 40 cm over 9 years 
  effects_CRI_kghay <- round( effects_CRI * 1e3 * (4/3) / 9, 0 ) # kgC ha-1 y-1
  cbind( treatments_CRI, effects_CRI_kghay )

  treatments_NIC <- c(
    "Ma01_PS_CI.txt"  , "Ma02_PS_CM.txt"  ,
    "Ma03_SSTR_CM.txt", "Ma04_SSTR_OI.txt",
    "Ma05_SGTR_CI.txt", "Ma06_SGTR_CM.txt", "Ma07_SGTR_OI.txt", "Ma08_SGTR_OM.txt",
    "Ma09_ILSS_CI.txt", "Ma10_ILSS_CM.txt", "Ma11_ILSS_OI.txt", "Ma12_ILSS_OM.txt",
    "Ma13_ILSG_CM.txt", "Ma14_ILSG_OI.txt" )
  effects_NIC    <- mNIC + c(
    aNIC_shade["FS"  ] + aNIC_fert["CI"],
    aNIC_shade["FS"  ] + aNIC_fert["CM"],
    aNIC_shade["SSTR"] + aNIC_fert["CM"],
    aNIC_shade["SSTR"] + aNIC_fert["OI"],
    aNIC_shade["SGTR"] + aNIC_fert["CI"],
    aNIC_shade["SGTR"] + aNIC_fert["CM"],
    aNIC_shade["SGTR"] + aNIC_fert["OI"],
    aNIC_shade["SGTR"] + aNIC_fert["OM"],
    aNIC_shade["ILSS"] + aNIC_fert["CI"],
    aNIC_shade["ILSS"] + aNIC_fert["CM"],
    aNIC_shade["ILSS"] + aNIC_fert["OI"],
    aNIC_shade["ILSS"] + aNIC_fert["OM"],
    aNIC_shade["ILSG"] + aNIC_fert["CM"],
    aNIC_shade["ILSG"] + aNIC_fert["OI"] )
  effects_NIC_kghay <- round( effects_NIC * 1e3 * (4/3) / 9, 0 ) # kgC ha-1 y-1
  cbind( treatments_NIC, effects_NIC_kghay )
```


## Results from BC

Unless otherwise indicated, all simulation results shown in this section are for the Maximum A Posteriori (MAP) paramater vector from a single multi-site calibration of CAF2021 on data from Turrialba and Masatepe.

Fig. \ref{fig:YieldsObsSimTurrialbaMasatepe} shows average observed coffee yield in the 32  treatments (18 from Turrialba, 14 from Masatepe) against N-fertilisation rate and against simulated yield.

```{r, out.width="100%", fig.cap="\\label{fig:YieldsObsSimTurrialbaMasatepe}Yields for the 32 treatments in Turrialba and Masatepe. Left: Observed yields against N-fertilisation level. Right: Observed yield vs. simulated yield."}
  load( fileTM )
  source(sitesettings_filenames[1]) # Knitting requires a model initialisation

  source('BC/BC_Yields.R')
  s.plot <- 1:nSites ; source('BC/BC_plot_YieldsAverage.R')
  # source('BC/BC_plot_YieldsAnnual.R')
```

Fig. \ref{fig:BalancesTurrialbaMasatepe} shows carbon and nitrogen balances in the 32 treatments (1:18 from Turrialba, 19:32 from Masatepe).

```{r, out.width="100%", fig.cap="\\label{fig:BalancesTurrialbaMasatepe}Carbon- and nitrogen-balances for 32 treatments. 1:18 = Turrialba, 19:32 = Masatepe. Simulations using the MAP parameter vector from Bayesian calibration."}
  load( fileTM )
  source(sitesettings_filenames[1]) # Knitting requires a model initialisation

  source('BC/BC_Balances.R')
  source('BC/BC_plot_Balances.R')
```

```{r}
  load( fileTM )
  source(sitesettings_filenames[1]) # Knitting requires a model initialisation

  # source('BC/BC_Final.R')
  # iNfixT     <- which(outputNames=="NfixT_f_hay")
  # iNleaching <- which(outputNames=="Nleaching_f_hay")

  source('BC/BC_FinalYearMean.R')
  iNfixT     <- which(outputNames=="NfixT_f")
  iNleaching <- which(outputNames=="Nleaching_f")

  par( mfrow=c(2,1), mar=c(3,2,2,0) )
  
  colbars <- c( "gray40"    , "gray80"    , "gray60"    , "gray100"   ,
                "gray40"    , "gray80"    , "gray60"    , "gray100"   ,
                "gray80"    , "gray60"    ,
                "gray80"    , "gray60"    ,
                "gray40"    , "gray80"    , "gray60"    , "gray100"   ,
                "gray40"    , "gray80"    ,
                "firebrick4", "firebrick2", 
                "firebrick2", "firebrick3",
                "firebrick4", "firebrick2", "firebrick3", "firebrick1", 
                "firebrick4", "firebrick2", "firebrick3", "firebrick1",
                "firebrick2", "firebrick3" )
  # barplot( as.matrix(outputFinalDay[,iNfixT]),
  barplot( as.matrix(outputFinalYearMean[,iNfixT]) * 1e4 * 365,
           main=paste( "Turrialba     ",
                       "N-FIXATION (kg N ha-1 y-1)",
                       "      Masatepe" ),
           col=colbars, beside=TRUE )
  # barplot( as.matrix(outputFinalDay[,iNleaching]),
  barplot( as.matrix(outputFinalYearMean[,iNleaching]) * 1e4 * 365,
           main="N-LEACHING (kg N ha-1 y-1)",
           col=colbars, beside=TRUE, names.arg=1:nSites )
```

```{r}
  load( fileTM )

  sA <- 1 ; sB <- 2 ; sC <- 3 ; sD <- 4
  source(sitesettings_filenames[sA]) ; params.MAP.A <- params.MAP.s( sA )
  output.MAP.A <- run_model( p=params.MAP.A )
  source(sitesettings_filenames[sB]) ; params.MAP.B <- params.MAP.s( sB )
  output.MAP.B <- run_model( p=params.MAP.B )
  source(sitesettings_filenames[sC]) ; params.MAP.C <- params.MAP.s( sC )
  output.MAP.C <- run_model( p=params.MAP.C )
  source(sitesettings_filenames[sD]) ; params.MAP.D <- params.MAP.s( sD )
  output.MAP.D <- run_model( p=params.MAP.D )
```

```{r}
  par( mfrow=c(2,4) )

  par(mar=c(3,3,3,0))
  plot_NbalanceSoil(output.MAP.A, title1="", title2="CI", ymax=800)
  par(mar=c(3,3,3,0))
  plot_NbalanceSoil(output.MAP.B, title1="", title2="CM", ymax=800)
  par(mar=c(3,3,3,0))
  plot_NbalanceSoil(output.MAP.C, title1="", title2="OI", ymax=800)
  par(mar=c(3,3,3,0))
  plot_NbalanceSoil(output.MAP.D, title1="", title2="OM", ymax=800)
```

## Sensitivity analyses

### N-leaching (parameter RNLEACH) 

We explore sensitivity of model outputs to the leaching-parameter 'RNLEACH'.

```{r, out.width="100%", fig.cap="\\label{fig:TurrialbaMasatepeYields2}Yields using the MAP parameter vector from Bayesian calibration, but with some additional parameter change(s)."}
  load( fileTM )
  source(sitesettings_filenames[1]) # Knitting requires a model initialisation

  set_parNames  <- c( "RNLEACH" )
  set_parValues <- c(  0.2      )
  source('BC/BC_Yields_set_par.R')
  source('BC/BC_plot_YieldsAverage.R')
```

```{r, out.width="100%", fig.cap="\\label{fig:TurrialbaMasatepeBalances2}Balances using the MAP parameter vector from Bayesian calibration, but with some additional parameter change(s)."}
  load( fileTM )
  source(sitesettings_filenames[1]) # Knitting requires a model initialisation

  source('BC/BC_Balances_set_par.R')
  source('BC/BC_plot_Balances.R')
```

### Deciduousness

```{r}
  load( fileTM )

  sA            <- 23 # Masatepe_05_SGTR_CI
  source(sitesettings_filenames[sA])
  params        <- params.MAP.s( sA )
  params.MAP.A  <- params
  params.MAP.A1 <- set_par( c("FTCLMINT(3)","TCLMAXT(3)"),
                            c( 0.2         , 650        ) )
  params.MAP.A2 <- set_par( c("FTCLMINT(3)","TCLMAXT(3)"),
                            c( 0.05        , 650        ) )
  params.MAP.A3 <- set_par( c("FTCLMINT(3)","TCLMAXT(3)"),
                            c( 0.2         , 365        ) )
  output.MAP.A  <- run_model( p=params.MAP.A  )
  output.MAP.A1 <- run_model( p=params.MAP.A1 )
  output.MAP.A2 <- run_model( p=params.MAP.A2 )
  output.MAP.A3 <- run_model( p=params.MAP.A3 )

  plot_output( list_output=list( output.MAP.A,
                                 output.MAP.A1, output.MAP.A2 ,output.MAP.A3),
               vars=c( "fTranT_t(3)", "LAIT_t(3)" ) )
```

### Impact of removing pruned leaves and branches

Comparison of leaving tree branches on the field after thinning and pruning (default) vs. removing them as harvest (customary in NIC and GTM): Fig. \ref{fig:Balances2}.

```{r Balances2, fig.height=6, fig.cap="\\label{fig:Balances2}Soil N- and C-balances at Masatepe in the ILSS_CI system. Top row: tree branches harvested and removed after pruning and thinning. Bottom row: branches left on the field as litter."}
  load( fileTM )
  sA <- 27 # Masatepe_09_ILSS_CI
  source(sitesettings_filenames[sA])
  params        <- params.MAP.s( sA )
  params.MAP.A  <- params
  params.MAP.A1 <- set_par( c("FHARVBT(1)","FHARVBT(2)","FHARVBT(3)"),
                            c( 0          , 0          , 0          ) )
  output.MAP.A  <- run_model( p=params.MAP.A  )
  output.MAP.A1 <- run_model( p=params.MAP.A1 )

  par( mar=c(3,3,3,0), mfrow=c(2,4) )
  plot_NbalanceSoil( output.MAP.A , title1="Soil N-balance MAP", title2="" )
  par( mar=c(3,3,3,0) )
  plot_CbalanceSoil( output.MAP.A , title1="Soil C-balance MAP", title2="" )
  par( mar=c(3,3,3,0) )
  plot_NbalanceSoil( output.MAP.A1, title1="Soil N-balance 1", title2="" )
  par( mar=c(3,3,3,0) )
  plot_CbalanceSoil( output.MAP.A1, title1="Soil C-balance 1", title2="" )
```

## Turrialba vs. Masatepe

```{r}
  load( fileTM )
  source(sitesettings_filenames[1]) # Knitting requires a model initialisation

  source('BC/BC_Yields.R')
  s.plot <-  1:18 ; source('BC/BC_plot_YieldsAverage.R')
  s.plot <- 19:32 ; source('BC/BC_plot_YieldsAverage.R')
```

### After a BC: comparing posterior with prior

```{r}
  load( fileTM )
  sTa             <- 13
  source(sitesettings_filenames[13]) # Turrialba_15_CE_AC
  params.Prior.Ta <- params
  params.MAP.Ta   <- params.MAP.s( sTa )
  output.Prior.Ta <- run_model( p=params.Prior.Ta )
  output.MAP.Ta   <- run_model( p=params.MAP.Ta )

  plot_output( list_output=list(output.Prior.Ta),
               vars       =c( "fTran(1)"    , "fNgrowth(1)", "DVS(1)"  ,
                              "SINKP(1)"    , "DayFl(1)"   , "PARMA(1)" ,
                              "harvDM_f_hay", "CT_f" ) )
  plot_output( list_output=list(output.MAP.Ta),
               vars       =c( "fTran(1)"    , "fNgrowth(1)", "DVS(1)"  ,
                              "SINKP(1)"    , "DayFl(1)"   , "PARMA(1)" ,
                              "harvDM_f_hay", "CT_f" ) )
```
