---
title: 'Modelling Coffee Agroforestry in Central America with CAF2021'
subtitle: 'Progress report II for project SEACAF, sub-contract B0554x4'
author:
- Marcel van Oijen^[Independent researcher, Edinburgh, UK - VanOijenMarcel@gmail.com]
date: '`r Sys.Date()`'
output:
  pdf_document:
    fig_crop: false
    fig_caption: yes
    keep_tex: no
    number_sections: yes
    toc: yes
  word_document:
    reference_docx: word-styles-reference-01.docx
  html_document: default
fontsize: 11pt
geometry: margin=1in
csl: environmental-modelling-and-software.csl
bibliography: [Avocado.bib,Banana.bib,MvO.bib]
---

```{r, include=FALSE}
  knitr::opts_chunk$set(echo=F,results="asis",warning=FALSE,message=FALSE)
```

```{r}
  plot_NbalanceSoil <- function( sim=output, title1="", title2=title1,
                                 ymax=NULL, verify=F ) {
    NinNames  <- c("Nfert_f", "NfixT_f", "NsenprunT_f", "Nsenprun_f")
    NoutNames <- c("Nleaching_f", "Nemission_f", "Nrunoff_f", "Nupt_f", "NuptT_f")
    nNin      <- length(NinNames) ; nNout  <- length(NoutNames)
    i.Nin     <- rep(NA,nNin)     ; i.Nout <- rep(NA,nNout)
    for(i in 1:nNin ) {i.Nin [i] <- which( outputNames==NinNames [i] ) }
    for(i in 1:nNout) {i.Nout[i] <- which( outputNames==NoutNames[i] ) }
    NinMean   <- colMeans(sim[,i.Nin])  * 1.e4 * 365 # kgN ha-1 y-1
    NoutMean  <- colMeans(sim[,i.Nout]) * 1.e4 * 365 # kgN ha-1 y-1
    if(is.null(ymax)) {
      y.max <- max( sum(NinMean), sum(NoutMean) )
    } else {
      y.max = ymax
    }
    leg <- NinNames
    barplot( as.matrix(NinMean),
             beside=F, ylim=c(0,y.max), col=1:length(leg),
             legend.text=leg,
             args.legend=list( title="Inputs (kg ha-1 y-1)", cex=0.8,
                               x="bottom", bg="white", inset=c(-0.3,0) ) )
    title(title1,adj=1)
    par(mar=c(3,0,3,3))
    leg <- NoutNames
    barplot( as.matrix(NoutMean),
             yaxt="n",
             beside=F, ylim=c(0,y.max), col=1:length(leg),
             legend.text=leg,
             args.legend=list( title="Outputs (kg ha-1 y-1)", cex=0.8,
                               x="bottom", bg="white", inset=c(-0.3,0) ) )
    title(title2,adj=0)
    if(verify) {
      Nsoil_f      <- sim[ , which( outputNames=="Nsoil_f") ] # kgN m-2
      D_Nsoil_f    <- Nsoil_f[NDAYS] - Nsoil_f[1]                # kgN m-2
      NinSum       <- colSums(sim[2:NDAYS,i.Nin ])            # kgN m-2
      NoutSum      <- colSums(sim[2:NDAYS,i.Nout])            # kgN m-2
      NinMinusNout <- sum(NinSum) - sum(NoutSum)
      cat( "VERIFYING THE N-BALANCE FOR THE SOIL (kgN m-2):",
           "\nState variable change: ", D_Nsoil_f,
           "\nInputs minus outputs : ", NinMinusNout )
    }
  }
```

```{r}
  plot_CbalanceSoil <- function( sim=output, title1="", title2=title1,
                                 ymax=NULL, verify=F ) {
    CinNames  <- c("CsenprunT_f", "Csenprun_f")
    CoutNames <- c("Rsoil_f", "Crunoff_f")
    nCin      <- length(CinNames) ; nCout  <- length(CoutNames)
    i.Cin     <- rep(NA,nCin)     ; i.Cout <- rep(NA,nCout)
    for(i in 1:nCin ) {i.Cin [i] <- which( outputNames==CinNames [i] ) }
    for(i in 1:nCout) {i.Cout[i] <- which( outputNames==CoutNames[i] ) }
    CinMean   <- colMeans(sim[,i.Cin])  * 1.e4 * 365 # kgC ha-1 y-1
    CoutMean  <- colMeans(sim[,i.Cout]) * 1.e4 * 365 # kgC ha-1 y-1
    if(is.null(ymax)) {
      y.max <- max( sum(CinMean), sum(CoutMean) )
    } else {
      y.max = ymax
    }
    leg <- CinNames
    barplot( as.matrix(CinMean),
             beside=F, ylim=c(0,y.max), col=1:length(leg),
             legend.text=leg,
             args.legend=list( title="Inputs (kg ha-1 y-1)", cex=0.8,
                               x="bottom", bg="white", inset=c(-0.3,0) ) )
    title(title1,adj=1)
    par(mar=c(3,0,3,3))
    leg <- CoutNames
    barplot( as.matrix(CoutMean),
             yaxt="n",
             beside=F, ylim=c(0,y.max), col=1:length(leg),
             legend.text=leg,
             args.legend=list( title="Outputs (kg ha-1 y-1)", cex=0.8,
                               x="bottom", bg="white", inset=c(-0.3,0) ) )
    title(title2,adj=0)
    if(verify) {
      Csoil_f   <- sim[ , which( outputNames=="Csoil_f") ] # kgC m-2 
      D_Csoil_f <- Csoil_f[NDAYS] - Csoil_f[1]                # kgC m-2
      CinSum        <- colSums(sim[2:NDAYS,i.Cin ])        # kgC m-2
      CoutSum       <- colSums(sim[2:NDAYS,i.Cout])        # kgC m-2
      CinMinusCout  <- sum(CinSum) - sum(CoutSum)
      cat( "VERIFYING THE C-BALANCE FOR THE SOIL (kgC m-2):",
           "\nState variable change: ", D_Csoil_f,
           "\nInputs minus outputs : ", CinMinusCout )
    }
  }
```

```{r}
  plot_H2ObalanceSoil <- function( sim=output, title1="", title2=title1,
                                   ymax=NULL, verify=F ) {
    WinNames  <- c("Rain_f")
    WoutNames <- c("Drain_f", "Runoff_f" , "Evap_f"    ,"Tran_f" , 
                   "TranT_f", "Rainint_f", "RainintT_f")
    nWin      <- length(WinNames) ; nWout  <- length(WoutNames)
    i.Win     <- rep(NA,nWin)     ; i.Wout <- rep(NA,nWout)
    for(i in 1:nWin ) {i.Win [i] <- which( outputNames==WinNames [i] ) }
    for(i in 1:nWout) {i.Wout[i] <- which( outputNames==WoutNames[i] ) }
    WinMean   <-    mean (sim[,i.Win])  # mm d-1
    WoutMean  <- colMeans(sim[,i.Wout]) # mm d-1
    if(is.null(ymax)) {
      y.max <- max( sum(WinMean), sum(WoutMean) )
    } else {
      y.max = ymax
    }
    leg <- WinNames
    barplot( as.matrix(WinMean),
             beside=F, ylim=c(0,y.max), col=1:length(leg),
             legend.text=leg,
             args.legend=list( title="Inputs (mm d-1)", cex=0.8,
                               x="bottom", bg="white", inset=c(-0.3,0) ) )
    title(title1,adj=1)
    par(mar=c(3,0,3,3))
    leg <- WoutNames
    barplot( as.matrix(WoutMean),
             yaxt="n",
             beside=F, ylim=c(0,y.max), col=1:length(leg),
             legend.text=leg,
             args.legend=list( title="Outputs (mm d-1)", cex=0.8,
                               x="bottom", bg="white", inset=c(-0.3,0) ) )
    title(title2,adj=0)
    if(verify) {
      WA_f   <- sim[ , which( outputNames=="WA_f") ] # mm
      D_WA_f <- WA_f[NDAYS] - WA_f[1]                   # mm
      WinSum        <-    sum (sim[2:NDAYS,i.Win ])  # mm
      WoutSum       <- colSums(sim[2:NDAYS,i.Wout])  # mm
      WinMinusWout  <- sum(WinSum) - sum(WoutSum)
      cat( "VERIFYING THE H2O-BALANCE FOR THE SOIL (mm):",
           "\nState variable change: ", D_WA_f,
           "\nInputs minus outputs : ", WinMinusWout )
    }
  }
```

```{r}
  plot_CbalanceCoffee <- function( sim=output, title1="", title2=title1,
                                   ymax=NULL, verify=F ) {
    CinNames  <- "gC_f"
    CoutNames <- c("dC_f", "prunC_f", "harvCP_f")
    nCin      <- length(CinNames) ; nCout  <- length(CoutNames)
    i.Cin     <- rep(NA,nCin)     ; i.Cout <- rep(NA,nCout)
    for(i in 1:nCin ) {i.Cin [i] <- which( outputNames==CinNames [i] ) }
    for(i in 1:nCout) {i.Cout[i] <- which( outputNames==CoutNames[i] ) }
    CinMean   <-    mean (sim[,i.Cin])  * 1.e4 * 365 # kgC ha-1 y-1
    CoutMean  <- colMeans(sim[,i.Cout]) * 1.e4 * 365 # kgC ha-1 y-1
    if(is.null(ymax)) {
      y.max <- max( sum(CinMean), sum(CoutMean) )
    } else {
      y.max = ymax
    }
    leg <- CinNames
    barplot( CinMean,
             beside=F, ylim=c(0,y.max), col=1:length(leg),
             legend.text=leg,
             args.legend=list( title="Inputs (kg ha-1 y-1)", cex=0.8,
                               x="bottom", bg="white", inset=c(-0.3,0) ) )
    title(title1,adj=1)
    par(mar=c(3,0,3,3))
    leg <- CoutNames
    barplot( as.matrix(CoutMean),
             yaxt="n",
             beside=F, ylim=c(0,y.max), col=1:length(leg),
             legend.text=leg,
             args.legend=list( title="Outputs (kg ha-1 y-1)", cex=0.8,
                               x="bottom", bg="white", inset=c(-0.3,0) ) )
    title(title2,adj=0)
    if(verify) {
      C_f          <- sim[ , which( outputNames=="C_f" ) ] # kgC m-2
      D_C_f        <- C_f[NDAYS] - C_f[1]                     # kgC m-2
      CinSum       <-    sum (sim[2:NDAYS,i.Cin ])         # kgC m-2
      CoutSum      <- colSums(sim[2:NDAYS,i.Cout])         # kgC m-2
      CinMinusCout <- sum(CinSum) - sum(CoutSum)
      cat( "VERIFYING THE C-BALANCE OF COFFEE (kgC m-2):",
           "\nState variable change: ", D_C_f,
           "\nInputs minus outputs : ", CinMinusCout )
    }
  }
```

```{r}
  plot_CbalanceSystem <- function( sim=output, title1="", title2=title1,
                                   ymax=NULL, verify=F ) {
    CinNames  <- c("gC_f"   , "gCT_f")
    CoutNames <- c("Rsoil_f", "Crunoff_f", "harvCP_f", "harvCPT_f", "harvCST_f")
    nCin      <- length(CinNames) ; nCout  <- length(CoutNames)
    i.Cin     <- rep(NA,nCin)     ; i.Cout <- rep(NA,nCout)
    for(i in 1:nCin ) {i.Cin [i] <- which( outputNames==CinNames [i] ) }
    for(i in 1:nCout) {i.Cout[i] <- which( outputNames==CoutNames[i] ) }
    CinMean   <- colMeans(sim[,i.Cin])  * 1.e4 * 365 # kgC ha-1 y-1
    CoutMean  <- colMeans(sim[,i.Cout]) * 1.e4 * 365 # kgC ha-1 y-1
    if(is.null(ymax)) {
      y.max <- max( sum(CinMean), sum(CoutMean) )
    } else {
      y.max = ymax
    }
    leg <- CinNames
    barplot( as.matrix(CinMean),
             beside=F, ylim=c(0,y.max), col=1:length(leg),
             legend.text=leg,
             args.legend=list( title="Inputs (kg ha-1 y-1)", cex=0.8,
                               x="bottom", bg="white", inset=c(-0.3,0) ) )
    title(title1,adj=1)
    par(mar=c(3,0,3,3))
    leg <- CoutNames
    barplot( as.matrix(CoutMean),
             yaxt="n",
             beside=F, ylim=c(0,y.max), col=1:length(leg),
             legend.text=leg,
             args.legend=list( title="Outputs (kg ha-1 y-1)", cex=0.8,
                               x="bottom", bg="white", inset=c(-0.3,0) ) )
    title(title2,adj=0)
    if(verify) {
      C_f      <- sim[ , which( outputNames=="C_f" )    ] # kgC m-2
      CT_f     <- sim[ , which( outputNames=="CT_f")    ] # kgC m-2
      Csoil_f  <- sim[ , which( outputNames=="Csoil_f") ] # kgC m-2 
      Csys_f   <- C_f + CT_f + Csoil_f                       # kgC m-2
      D_Csys_f <- Csys_f[NDAYS] - Csys_f[1]                  # kgC m-2
      CinSum       <- colSums(sim[2:NDAYS,i.Cin ])        # kgC m-2
      CoutSum      <- colSums(sim[2:NDAYS,i.Cout])        # kgC m-2
      CinMinusCout <- sum(CinSum) - sum(CoutSum)
      cat( "VERIFYING THE C-BALANCE FOR THE SYSTEM (kgC m-2):",
           "\nState variable change: ", D_Csys_f,
           "\nInputs minus outputs : ", CinMinusCout )
    }
  }
```

```{r}
  plot_CdistributionCoffee <- function( sim=output ) {
    Time <- sim[,1]
    i.CP <- which( outputNames=="CP_f" ) ; CP <- sim[,i.CP]
    i.CL <- which( outputNames=="CL_f" ) ; CL <- sim[,i.CL]
    i.CW <- which( outputNames=="CW_f" ) ; CW <- sim[,i.CW]
    i.CR <- which( outputNames=="CR_f" ) ; CR <- sim[,i.CR]
    plot( Time, CR+CW+CL+CP,
          main="Carbon in coffee (kg C m-2)",
          xlab="", ylab="", type="l", ylim=c(0,max(CR+CW+CL+CP)) )
    points( Time, CR+CW+CL, type="l", col="yellow" )
    points( Time, CR+CW   , type="l", col="green" )
    points( Time, CR      , type="l", col="red" )
    legend( "bottom", cex=0.7, lty=1, bg="white",
            col=c("black","yellow","green","red"),
            legend=c("+ CP: Beans",
                     "+ CL: Leaves",
                     "+ CW: Wood",
                     "   CR: Roots" ) )
  }
```

```{r}
  plot_CdistributionTrees <- function( sim=output, it=1:3 ) {
    Time <- sim[,1]
    i.CPT <- sapply( 1:3, function(i){which( outputNames==paste0("CPT_t(",i,")"))} )
    i.CLT <- sapply( 1:3, function(i){which( outputNames==paste0("CLT_t(",i,")"))} )
    i.CBT <- sapply( 1:3, function(i){which( outputNames==paste0("CBT_t(",i,")"))} )
    i.CST <- sapply( 1:3, function(i){which( outputNames==paste0("CST_t(",i,")"))} )
    i.CRT <- sapply( 1:3, function(i){which( outputNames==paste0("CRT_t(",i,")"))} )
    for(t in it) {
      CPT   <- sim[,i.CPT[t]] ; CLT <- sim[,i.CLT[t]] ; CBT <- sim[,i.CBT[t]]
      CST   <- sim[,i.CST[t]] ; CRT <- sim[,i.CRT[t]]
      y.max <- max(CRT+CST+CBT+CLT+CPT)
      plot( Time, CRT+CST+CBT+CLT+CPT, ylim=c(0,y.max),
            main=paste0("Carbon in tree sp. ",it," (kg C m-2)"),
            xlab="", ylab="", type="l" )
      points( Time, CRT+CST+CBT+CLT, type="l", col="yellow" )
      points( Time, CRT+CST+CBT    , type="l", col="green"  )
      points( Time, CRT+CST        , type="l", col="red"    )
      points( Time, CRT            , type="l", col="blue"   )
      legend( "bottom", cex=0.7, lty=1, bg="white",
              col=c("black","yellow","green","red","blue"),
              legend=c("+ CPT: Fruits",
                       "+ CLT: Leaves",
                       "+ CBT: Branches",
                       "+ CST: Stems",
                       "   CRT: Roots" ) )
    }
  }
```

```{r}
  params.MAP.s <- function(s) {
    params_BC_MAP   <- scparMAP_BC  * sc
    params          <- list_params        [[s]]
    ip_BC_s         <- ip_BC_site         [[s]]
    icol_pChain_s   <- icol_pChain_site   [[s]]
    params[ip_BC_s] <- params_BC_MAP      [icol_pChain_s]
    return( params )
  }
```


# Masatepe

Unless otherwise indicated, all results shown in this section are for the Maximum A Posteriori (MAP) paramater vector from calibrating CAF2021 on data from Masatepe.

Fig. \ref{fig:YieldsObsSim} shows observed and simulated variation of coffee production in the 14 simulated treatments of the Masatepe experiment.

```{r}
  load('BC_07_51.RData')
  source("initialisation/initialise_CAF2021_Masatepe_05_SGTR_CI.R")

  params.Prior.5 <- params
  output.Prior.5 <- run_model( p=params.Prior.5 )
  
  params.MAP.5   <- params.MAP.s( 5 )
  output.MAP.5   <- run_model( p=params.MAP.5 )
```

```{r}
  load('BC_07_51.RData')
  source("initialisation/initialise_CAF2021_Masatepe_09_ILSS_CI.R")

  params.Prior.9 <- params
  output.Prior.9 <- run_model( p=params.Prior.9 )
  
  params.MAP.9   <- params.MAP.s( 9 )
  output.MAP.9   <- run_model( p=params.MAP.9 )
```

```{r, out.width="100%", fig.cap="\\label{fig:YieldsObsSim}Simulated vs. observed annual yields for the 14 treatments in Masatepe 2005-2014. Left: all 140 recorded and simulated yields. Right: average yield for each of the treatments."}
  load('BC_07_51.RData')
  source('BC/BC_plot_yields.R')
```

```{r}
  plot_output( list_output=list(output.Prior.9),
               vars       =c( "fTran(1)"    , "fNgrowth(1)", "DVS(1)"  ,
                              "SINKP(1)"    , "DayFl(1)"   , "PARMA(1)" ,
                              "harvDM_f_hay", "CT_f" ) )
  plot_output( list_output=list(output.MAP.9),
               vars       =c( "fTran(1)"    , "fNgrowth(1)", "DVS(1)"  ,
                              "SINKP(1)"    , "DayFl(1)"   , "PARMA(1)" ,
                              "harvDM_f_hay", "CT_f" ) )
```

Biogeochemical balances for Masatepe (Nicaragua) are shown in Fig. \ref{fig:Balances}.

```{r Balances, fig.height=6, fig.cap="\\label{fig:Balances}Biogeochemical balances for nitrogen, carbon and water at Masatepe in the ILSS_CI system (shading by both Inga laurina and Samanea saman; Fertilisation-mode CI). Left bar from each pair: gains; right bar: losses. All rates are averages for the whole period of simulation."}
  par( mar=c(3,3,3,0), mfrow=c(2,4) )
  plot_NbalanceSoil  (output.MAP.9, title1="Soil N-balance"  , title2="")
  par( mar=c(3,3,3,0) )
  plot_CbalanceSoil  (output.MAP.9, title1="Soil C-balance"  , title2="")
  par( mar=c(3,3,3,0) )
  plot_H2ObalanceSoil(output.MAP.9, title1="Soil H2O-balance", title2="")
  par( mar=c(3,3,3,0) )
  plot_CbalanceSystem(output.MAP.9, title1="System C-balance", title2="")
```

Comparison of leaving tree branches on the field after thinning and pruning (default) vs. removing them as harvest (customary in NIC and GTM): Fig. \ref{fig:Balances2}.

```{r Balances2, fig.height=6, fig.cap="\\label{fig:Balances2}Soil N- and C-balances at Masatepe in the ILSS_CI system. Top row: tree branches left as litter after pruning and thinning. Bottom row: branches harvested."}
  params  <- params.MAP.9
  params1 <- set_par( c("FHARVBT(1)","FHARVBT(2)","FHARVBT(3)"),
                      c( 0          , 0          , 0          ) )
  params2 <- set_par( c("FHARVBT(1)","FHARVBT(2)","FHARVBT(3)"),
                      c( 1          , 1          , 1          ) )
  output1 <- run_model( p=params1 )
  output2 <- run_model( p=params2 )

  par( mar=c(3,3,3,0), mfrow=c(2,4) )
  plot_NbalanceSoil( output1, title1="Soil N-balance 1", title2="" )
  par( mar=c(3,3,3,0) )
  plot_CbalanceSoil( output1, title1="Soil C-balance 1", title2="" )
  par( mar=c(3,3,3,0) )
  plot_NbalanceSoil( output2, title1="Soil N-balance 2", title2="" )
  par( mar=c(3,3,3,0) )
  plot_CbalanceSoil( output2, title1="Soil C-balance 2", title2="" )
```

Fig. \ref{fig:Nbalance4Nlevels} shows how the soil N-balance is affected by N-fertilisation.

```{r Nbalance4Nlevels, fig.height=6, fig.cap="\\label{fig:Nbalance4Nlevels}Soil nitrogen balances for 4 different treatments at Masatepe in the ILSS system (shading by both Inga laurina and Samanea saman). Gains on the left, losses on the right."}
  par( mfrow=c(2,4) )
  par(mar=c(3,3,3,0))
  # source("initialisation/initialise_CAF2021_Masatepe_09_ILSS_CI.R")
  # params <- params.MAP.s(9)
  # output <- run_model()
  # plot_NbalanceSoil(output, title1="", title2="CI", ymax=800)
  plot_NbalanceSoil(output.MAP.9, title1="", title2="CI", ymax=800)
  par(mar=c(3,3,3,0))
  source("initialisation/initialise_CAF2021_Masatepe_10_ILSS_CM.R")
  params <- params.MAP.s(10)
  output <- run_model()
  plot_NbalanceSoil(output, title1="", title2="CM", ymax=800)
  par(mar=c(3,3,3,0))
  source("initialisation/initialise_CAF2021_Masatepe_11_ILSS_OI.R")
  params <- params.MAP.s(11)
  output <- run_model()
  plot_NbalanceSoil(output, title1="", title2="OI", ymax=800)
  par(mar=c(3,3,3,0))
  source("initialisation/initialise_CAF2021_Masatepe_12_ILSS_OM.R")
  params <- params.MAP.s(12)
  output <- run_model()
  plot_NbalanceSoil(output, title1="", title2="OM", ymax=800)
```

# Deciduousness

```{r}
  plot_output( list_output=list(output.MAP.5),
               vars       =c( "LAIT_t(1)", "LAIT_t(2)", "LAIT_t(3)" ) )

  plot_output( list_output=list(output.MAP.9),
               vars       =c( "LAIT_t(1)", "LAIT_t(2)", "LAIT_t(3)" ) )

```

```{r, fig.height=6, fig.cap="\\label{fig:Deciduousness}Soil N- and C-balances at Masatepe in the ILSS_CI system. Top row: tree branches left as litter after pruning and thinning. Bottom row: branches harvested."}
  params    <- params.MAP.5
  paramsM5a <- set_par( c("FTCLMINT(3)","TCLMAXT(3)"),
                        c( 0.2         , 650        ) )
  paramsM5b <- set_par( c("FTCLMINT(3)","TCLMAXT(3)"),
                        c( 0.05        , 650        ) )
  paramsM5c <- set_par( c("FTCLMINT(3)","TCLMAXT(3)"),
                        c( 0.2         , 365        ) )
  
  source("initialisation/initialise_CAF2021_Masatepe_05_SGTR_CI.R")
  output.MAP.5a <- run_model( p=paramsM5a )
  output.MAP.5b <- run_model( p=paramsM5b )
  output.MAP.5c <- run_model( p=paramsM5c )

  plot_output( list_output=list(output.MAP.5,
                                output.MAP.5a,output.MAP.5b ,output.MAP.5c),
               vars=c( "LAIT_t(3)" ) )

  plot_output( list_output=list(output.MAP.5,
                                output.MAP.5a,output.MAP.5b ,output.MAP.5c),
               vars=c( "fTranT_t(3)" ) )
```
