---
title: 'Modelling Coffee Agroforestry in Central America with CAF2021'
subtitle: 'Progress report III for project SEACAF, sub-contract B0554x4'
author:
- Marcel van Oijen^[Independent researcher, Edinburgh, UK - VanOijenMarcel@gmail.com]
date: '`r Sys.Date()`'
output:
  pdf_document:
    fig_crop: false
    fig_caption: yes
    keep_tex: no
    number_sections: yes
    toc: yes
  word_document:
    reference_docx: word-styles-reference-01.docx
  html_document: default
fontsize: 11pt
geometry: margin=1in
csl: environmental-modelling-and-software.csl
bibliography: [Avocado.bib,Banana.bib,SEACAF.bib]
---

```{r, include=FALSE}
  knitr::opts_chunk$set(echo=F,results="asis",warning=FALSE,message=FALSE)
  library(rworldmap)
  library(rworldxtra)
  library(raster)
  library(tidyverse)
```

```{r}
  # fileTM     <- "BC_Turrialba_Masatepe_09_08.RData"
  filesTM <- file.info(list.files(pattern="^BC_Turrialba_Masatepe.*\\.RData$"))
  filesTM <- filesTM[ with(filesTM,order(as.POSIXct(mtime))), ]
  fileTM  <- tail( rownames(filesTM[1]), 1 )
  load( fileTM )
  
  # fileTM_MAP <- "CAF2021_parMAP_09_08.rds"
  filesTM_MAP <- file.info(list.files(pattern="^CAF2021_parMAP.*\\.rds$"))
  filesTM_MAP <- filesTM_MAP[ with(filesTM_MAP,order(as.POSIXct(mtime))), ]
  fileTM_MAP  <- tail( rownames(filesTM_MAP[1]), 1 )
  parMAP      <- readRDS( fileTM_MAP )

  # THE FOLLOWING LINES LOAD THE MAP FROM AN OLDER MODEL VERSION WITH
  # FEWER PARAMATERS, AND CONSTRUCT THE MAP FOR THE CURRENT VERSION.
  # parMAP.old       <- readRDS( fileTM_MAP )
  # np.old           <- dim(parMAP.old)[1]
  # source('initialisation/set_CAF2021_Turrialba.R')
  # np               <- length( params )
  # parMAP           <- matrix( NA, nrow=np, ncol=nSites )
  # rownames(parMAP) <- names_params
  # colnames(parMAP) <- paste0( "s", 1:nSites )
  # for(p in 1:np.old) {
  #   prow          <- which( startsWith( rownames(parMAP),
  #                                       rownames(parMAP.old)[p] ) )
  #   for(r in prow) { parMAP[r,] <- parMAP.old[p,] }
  # }
```

# WorldClim

```{r}
  dir.f           <- "data/Farms SEACAF/"
  file_coords_C.f <- "coordinates_CR.csv"
  file_coords_G.f <- "coordinates_G.csv"
  
  dir_WC      <- "weather/WorldClim/"
  dir_WC_prec <- paste0( dir_WC, "prec/" ) # Monthly climatic means 1970-2000
  dir_WC_srad <- paste0( dir_WC, "srad/" ) # Monthly climatic means 1970-2000
  dir_WC_tmax <- paste0( dir_WC, "tmax/" ) # Monthly climatic means 1970-2000
  dir_WC_tmin <- paste0( dir_WC, "tmin/" ) # Monthly climatic means 1970-2000
  dir_WC_vapr <- paste0( dir_WC, "vapr/" ) # Monthly climatic means 1970-2000
  dir_WC_wind <- paste0( dir_WC, "wind/" ) # Monthly climatic means 1970-2000
```

```{r}
  df_C.f  <- read.csv( paste0( dir.f, file_coords_C.f ) )
  df_G.f  <- read.csv( paste0( dir.f, file_coords_G.f ) )
  
  df_C.f  <- df_C.f %>%
    rename( code=code_farm_new, lat=Latitud    , lon=Longitud ) %>%
    mutate( code=code+1000 ) %>%
    dplyr::select( code, lat, lon )
  df_G.f  <- df_G.f %>%
    rename( code=CODIGO.SEACAF, lat=decimal_LAT, lon=decimal_LONG ) %>%
    mutate( code=code+2000 ) %>%
    dplyr::select( code, lat, lon )
  df_CG.f <- df_C.f %>% full_join( df_G.f )
  
  coords_C.f  <- cbind( lon=df_C.f$lon, lat=df_C.f$lat )
  coords_G.f  <- cbind( lon=df_G.f$lon, lat=df_G.f$lat )
  coords_CG.f <- rbind( coords_C.f, coords_G.f )

  n_CG.f <- dim(coords_CG.f)[1]
  n_C.f  <- dim(coords_C.f) [1] ; n_G.f <- dim(coords_G.f)[1]
  i_C.f  <- 1:n_C.f             ; i_G.f <- (n_C.f+1):n_CG.f
```

See Fig. \ref{fig:MapFarms}.

```{r, fig.cap="\\label{fig:MapFarms}Locations of SEACAF farms in Costa Rica and Guatemala."}
  worldmap <- getMap(resolution = "high")
  plot( worldmap,
        col="lightgrey", border="darkgray",
        xlim=c(-93,-83), ylim=c(8,18),
        bg="aliceblue", asp=1 )
  points( coords_C.f, col="red" , pch=1, cex=0.2 )
  points( coords_G.f, col="blue", pch=1, cex=0.2 )
```

```{r}
  spdf_C   <- getData('GADM', country="CRI", level=0)
  spdf_C   <- crop(spdf_C, extent(-86,-82, 8, 12))
  spdf_C.f <- crop(spdf_C, extent(-84.6,-83.5, 9.5, 10.2))
  spdf_G   <- getData('GADM', country="GTM", level=0)
  spdf_G.f <- crop(spdf_G, extent(-92.1,-90.4,14.4, 15.1))
  
  ext_C    <- extent( spdf_C ) ; ext_C.f <- extent( spdf_C.f )
  ext_G    <- extent( spdf_G ) ; ext_G.f <- extent( spdf_G.f )
```

```{r}
  r_worldclim_alt_SE <- getData( 'worldclim', var='alt',
                                 res=0.5, lon=-83.51, lat= 9.58 )
  r_worldclim_alt_NW <- getData( 'worldclim', var='alt',
                                 res=0.5, lon=-92.07, lat=15.09 )
  alt_C    <- crop( r_worldclim_alt_SE, ext_C )
  alt_G    <- crop( r_worldclim_alt_NW, ext_G )
  # alt_C.f  <- raster::extract( r_worldclim_alt_SE, coords_C.f )
  # alt_G.f  <- raster::extract( r_worldclim_alt_NW, coords_G.f )
  alt_C.f  <- raster::extract( alt_C, coords_C.f )
  alt_G.f  <- raster::extract( alt_G, coords_G.f )
  alt_CG.f <- c( alt_C.f, alt_G.f )
```
    
```{r}
  code_C <- df_C.f$code - 1000
  code_G <- df_G.f$code - 2000
  x_C.f <- coords_C.f[,"lon"] ; y_C.f <- coords_C.f[,"lat"] 
  x_G.f <- coords_G.f[,"lon"] ; y_G.f <- coords_G.f[,"lat"] 

  plot_C.f <- function() {
    plot  ( spdf_C, add=T )
    points( x_C.f, y_C.f, pch=1, cex=0.5)
    # text  ( x_C.f, y_C.f, labels=code_C, pos=2, cex=0.5)
  }

  plot_G.f <- function() {
    plot  ( spdf_G, add=T )
    points( x_G.f, y_G.f, pch=1, cex=0.5)
    # text  ( x_G.f, y_G.f, labels=code_C, pos=2, cex=0.5)
  }
```

## RasterStack approach

See https://www.benjaminbell.co.uk/2018/02/rasterstacks-and-rasterplot.html.

```{r}
  prec <- stack( list.files( dir_WC_prec, ".tif", full.names=T ) )
  srad <- stack( list.files( dir_WC_srad, ".tif", full.names=T ) )
  tmax <- stack( list.files( dir_WC_tmax, ".tif", full.names=T ) )
  tmin <- stack( list.files( dir_WC_tmin, ".tif", full.names=T ) )
  vapr <- stack( list.files( dir_WC_vapr, ".tif", full.names=T ) )
  wind <- stack( list.files( dir_WC_wind, ".tif", full.names=T ) )

  month <- c( "Jan", "Feb", "Mar", "Apr", "May", "Jun",
              "Jul", "Aug", "Sep", "Oct", "Nov", "Dec" )
  names(prec) <- names(srad) <- names(tmax) <-
  names(tmin) <- names(vapr) <- names(wind) <- month
```

```{r}
  monl    <- c( 31, 28.25, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31 )

  GR_CG.f   <- round( raster::extract(srad, coords_CG.f) / 1000, 1 )
  TMIN_CG.f <- raster::extract(tmin, coords_CG.f)
  TMAX_CG.f <- raster::extract(tmax, coords_CG.f)
  VP_CG.f   <- raster::extract(vapr, coords_CG.f)
  WN_CG.f   <- raster::extract(wind, coords_CG.f)
  RAIN_CG.f <- raster::extract(prec, coords_CG.f)
    for(m in 1:12) RAIN_CG.f[,m] <- round( RAIN_CG.f[,m] / monl[m], 2 )
  
  GR_C.f   <- GR_CG.f  [ i_C.f, ] ; GR_G.f   <- GR_CG.f  [ i_G.f, ]
  TMIN_C.f <- TMIN_CG.f[ i_C.f, ] ; TMIN_G.f <- TMIN_CG.f[ i_G.f, ]
  TMAX_C.f <- TMAX_CG.f[ i_C.f, ] ; TMAX_G.f <- TMAX_CG.f[ i_G.f, ]
  VP_C.f   <- VP_CG.f  [ i_C.f, ] ; VP_G.f   <- VP_CG.f  [ i_G.f, ]
  WN_C.f   <- WN_CG.f  [ i_C.f, ] ; WN_G.f   <- WN_CG.f  [ i_G.f, ]
  RAIN_C.f <- RAIN_CG.f[ i_C.f, ] ; RAIN_G.f <- RAIN_CG.f[ i_G.f, ]
```

```{r}
  prec_C <- crop(prec, ext_C) ; prec_G <- crop(prec, ext_G)
  srad_C <- crop(srad, ext_C) ; srad_G <- crop(srad, ext_G)
  tmax_C <- crop(tmax, ext_C) ; tmax_G <- crop(tmax, ext_G)
  tmin_C <- crop(tmin, ext_C) ; tmin_G <- crop(tmin, ext_G)
  vapr_C <- crop(vapr, ext_C) ; vapr_G <- crop(vapr, ext_G)
  wind_C <- crop(wind, ext_C) ; wind_G <- crop(wind, ext_G)
```

```{r}
  tempcol <- colorRampPalette( c("purple", "blue", "skyblue", "green" ,
                   "lightgreen", "yellow", "orange", "red", "darkred") )
  plot( prec_C, main=month, col=rainbow(100,end=0.7),
        zlim=c(0,800), nc=3, nr=4 )
```

```{r}
  par( mfrow=c(1,2), mar=c(3,3,3,5) )

  plot( alt_C, main="alt_C", addfun=plot_C.f, zlim=c(0,4000) )
  plot( alt_G, main="alt_G", addfun=plot_G.f, zlim=c(0,4000) )
```

```{r}
  par( mfrow=c(2,6), mar=c(2,2,2,1) )

  plot  ( alt_C.f, GR_C.f  [,7], ylim=range(GR_CG.f)  , main="GR_C.f" )
  points( alt_C.f, GR_C.f  [,1], col="red" )
  plot  ( alt_C.f, TMIN_C.f[,7], ylim=range(TMIN_CG.f), main="TMIN_C.f" )
  points( alt_C.f, TMIN_C.f[,1], col="red" )
  plot  ( alt_C.f, TMAX_C.f[,7], ylim=range(TMAX_CG.f), main="TMAX_C.f" )
  points( alt_C.f, TMAX_C.f[,1], col="red" )
  plot  ( alt_C.f, VP_C.f  [,7], ylim=range(VP_CG.f)  , main="VP_C.f" )
  points( alt_C.f, VP_C.f  [,1], col="red" )
  plot  ( alt_C.f, WN_C.f  [,7], ylim=range(WN_CG.f)  , main="WN_C.f" )
  points( alt_C.f, WN_C.f  [,1], col="red" )
  plot  ( alt_C.f, RAIN_C.f[,7], ylim=range(RAIN_CG.f), main="RAIN_C.f" )
  points( alt_C.f, RAIN_C.f[,1], col="red" )
  
  plot  ( alt_G.f, GR_G.f  [,7], ylim=range(GR_CG.f)  , main="GR_G.f" )
  points( alt_G.f, GR_G.f  [,1], col="red" )
  plot  ( alt_G.f, TMIN_G.f[,7], ylim=range(TMIN_CG.f), main="TMIN_G.f" )
  points( alt_G.f, TMIN_G.f[,1], col="red" )
  plot  ( alt_G.f, TMAX_G.f[,7], ylim=range(TMAX_CG.f), main="TMAX_G.f" )
  points( alt_G.f, TMAX_G.f[,1], col="red" )
  plot  ( alt_G.f, VP_G.f  [,7], ylim=range(VP_CG.f)  , main="VP_G.f" )
  points( alt_G.f, VP_G.f  [,1], col="red" )
  plot  ( alt_G.f, WN_G.f  [,7], ylim=range(WN_CG.f)  , main="WN_G.f" )
  points( alt_G.f, WN_G.f  [,1], col="red" )
  plot  ( alt_G.f, RAIN_G.f[,7], ylim=range(RAIN_CG.f), main="RAIN_G.f" )
  points( alt_G.f, RAIN_G.f[,1], col="red" )
```



## RasterLayer approach

See https://www.benjaminbell.co.uk/2018/01/extracting-data-and-making-climate-maps.html.

```{r}
  prec01 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_01.tif" ) )
  prec02 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_02.tif" ) )
  prec03 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_03.tif" ) )
  prec04 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_04.tif" ) )
  prec05 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_05.tif" ) )
  prec06 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_06.tif" ) )
  prec07 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_07.tif" ) )
  prec08 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_08.tif" ) )
  prec09 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_09.tif" ) )
  prec10 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_10.tif" ) )
  prec11 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_11.tif" ) )
  prec12 <- raster( paste0( dir_WC_prec, "wc2.1_30s_prec_12.tif" ) )
  
  srad01 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_01.tif" ) )
  srad02 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_02.tif" ) )
  srad03 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_03.tif" ) )
  srad04 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_04.tif" ) )
  srad05 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_05.tif" ) )
  srad06 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_06.tif" ) )
  srad07 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_07.tif" ) )
  srad08 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_08.tif" ) )
  srad09 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_09.tif" ) )
  srad10 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_10.tif" ) )
  srad11 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_11.tif" ) )
  srad12 <- raster( paste0( dir_WC_srad, "wc2.1_30s_srad_12.tif" ) )
  
  tmax01 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_01.tif" ) )
  tmax02 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_02.tif" ) )
  tmax03 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_03.tif" ) )
  tmax04 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_04.tif" ) )
  tmax05 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_05.tif" ) )
  tmax06 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_06.tif" ) )
  tmax07 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_07.tif" ) )
  tmax08 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_08.tif" ) )
  tmax09 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_09.tif" ) )
  tmax10 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_10.tif" ) )
  tmax11 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_11.tif" ) )
  tmax12 <- raster( paste0( dir_WC_tmax, "wc2.1_30s_tmax_12.tif" ) )
  
  tmin01 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_01.tif" ) )
  tmin02 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_02.tif" ) )
  tmin03 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_03.tif" ) )
  tmin04 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_04.tif" ) )
  tmin05 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_05.tif" ) )
  tmin06 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_06.tif" ) )
  tmin07 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_07.tif" ) )
  tmin08 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_08.tif" ) )
  tmin09 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_09.tif" ) )
  tmin10 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_10.tif" ) )
  tmin11 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_11.tif" ) )
  tmin12 <- raster( paste0( dir_WC_tmin, "wc2.1_30s_tmin_12.tif" ) )
  
  vapr01 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_01.tif" ) )
  vapr02 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_02.tif" ) )
  vapr03 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_03.tif" ) )
  vapr04 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_04.tif" ) )
  vapr05 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_05.tif" ) )
  vapr06 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_06.tif" ) )
  vapr07 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_07.tif" ) )
  vapr08 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_08.tif" ) )
  vapr09 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_09.tif" ) )
  vapr10 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_10.tif" ) )
  vapr11 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_11.tif" ) )
  vapr12 <- raster( paste0( dir_WC_vapr, "wc2.1_30s_vapr_12.tif" ) )
  
  wind01 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_01.tif" ) )
  wind02 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_02.tif" ) )
  wind03 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_03.tif" ) )
  wind04 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_04.tif" ) )
  wind05 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_05.tif" ) )
  wind06 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_06.tif" ) )
  wind07 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_07.tif" ) )
  wind08 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_08.tif" ) )
  wind09 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_09.tif" ) )
  wind10 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_10.tif" ) )
  wind11 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_11.tif" ) )
  wind12 <- raster( paste0( dir_WC_wind, "wc2.1_30s_wind_12.tif" ) )
```

```{r}
  prec.data        <- df_CG.f
  prec.data$prec01 <- raster::extract(prec01, coords_CG.f) / 31
  prec.data$prec02 <- raster::extract(prec02, coords_CG.f) / 28
  prec.data$prec03 <- raster::extract(prec03, coords_CG.f) / 31
  prec.data$prec04 <- raster::extract(prec04, coords_CG.f) / 30
  prec.data$prec05 <- raster::extract(prec05, coords_CG.f) / 31
  prec.data$prec06 <- raster::extract(prec06, coords_CG.f) / 30
  prec.data$prec07 <- raster::extract(prec07, coords_CG.f) / 31
  prec.data$prec08 <- raster::extract(prec08, coords_CG.f) / 31
  prec.data$prec09 <- raster::extract(prec09, coords_CG.f) / 30
  prec.data$prec10 <- raster::extract(prec10, coords_CG.f) / 31
  prec.data$prec11 <- raster::extract(prec11, coords_CG.f) / 30
  prec.data$prec12 <- raster::extract(prec12, coords_CG.f) / 31
  
  srad.data        <- df_CG.f 
  srad.data$srad01 <- raster::extract(srad01, coords_CG.f) / 1000
  srad.data$srad02 <- raster::extract(srad02, coords_CG.f) / 1000
  srad.data$srad03 <- raster::extract(srad03, coords_CG.f) / 1000
  srad.data$srad04 <- raster::extract(srad04, coords_CG.f) / 1000
  srad.data$srad05 <- raster::extract(srad05, coords_CG.f) / 1000
  srad.data$srad06 <- raster::extract(srad06, coords_CG.f) / 1000
  srad.data$srad07 <- raster::extract(srad07, coords_CG.f) / 1000
  srad.data$srad08 <- raster::extract(srad08, coords_CG.f) / 1000
  srad.data$srad09 <- raster::extract(srad09, coords_CG.f) / 1000
  srad.data$srad10 <- raster::extract(srad10, coords_CG.f) / 1000
  srad.data$srad11 <- raster::extract(srad11, coords_CG.f) / 1000
  srad.data$srad12 <- raster::extract(srad12, coords_CG.f) / 1000
  
  tmax.data        <- df_CG.f 
  tmax.data$tmax01 <- raster::extract(tmax01, coords_CG.f)
  tmax.data$tmax02 <- raster::extract(tmax02, coords_CG.f)
  tmax.data$tmax03 <- raster::extract(tmax03, coords_CG.f)
  tmax.data$tmax04 <- raster::extract(tmax04, coords_CG.f)
  tmax.data$tmax05 <- raster::extract(tmax05, coords_CG.f)
  tmax.data$tmax06 <- raster::extract(tmax06, coords_CG.f)
  tmax.data$tmax07 <- raster::extract(tmax07, coords_CG.f)
  tmax.data$tmax08 <- raster::extract(tmax08, coords_CG.f)
  tmax.data$tmax09 <- raster::extract(tmax09, coords_CG.f)
  tmax.data$tmax10 <- raster::extract(tmax10, coords_CG.f)
  tmax.data$tmax11 <- raster::extract(tmax11, coords_CG.f)
  tmax.data$tmax12 <- raster::extract(tmax12, coords_CG.f)
  
  tmin.data        <- df_CG.f 
  tmin.data$tmin01 <- raster::extract(tmin01, coords_CG.f)
  tmin.data$tmin02 <- raster::extract(tmin02, coords_CG.f)
  tmin.data$tmin03 <- raster::extract(tmin03, coords_CG.f)
  tmin.data$tmin04 <- raster::extract(tmin04, coords_CG.f)
  tmin.data$tmin05 <- raster::extract(tmin05, coords_CG.f)
  tmin.data$tmin06 <- raster::extract(tmin06, coords_CG.f)
  tmin.data$tmin07 <- raster::extract(tmin07, coords_CG.f)
  tmin.data$tmin08 <- raster::extract(tmin08, coords_CG.f)
  tmin.data$tmin09 <- raster::extract(tmin09, coords_CG.f)
  tmin.data$tmin10 <- raster::extract(tmin10, coords_CG.f)
  tmin.data$tmin11 <- raster::extract(tmin11, coords_CG.f)
  tmin.data$tmin12 <- raster::extract(tmin12, coords_CG.f)
  
  vapr.data        <- df_CG.f 
  vapr.data$vapr01 <- raster::extract(vapr01, coords_CG.f)
  vapr.data$vapr02 <- raster::extract(vapr02, coords_CG.f)
  vapr.data$vapr03 <- raster::extract(vapr03, coords_CG.f)
  vapr.data$vapr04 <- raster::extract(vapr04, coords_CG.f)
  vapr.data$vapr05 <- raster::extract(vapr05, coords_CG.f)
  vapr.data$vapr06 <- raster::extract(vapr06, coords_CG.f)
  vapr.data$vapr07 <- raster::extract(vapr07, coords_CG.f)
  vapr.data$vapr08 <- raster::extract(vapr08, coords_CG.f)
  vapr.data$vapr09 <- raster::extract(vapr09, coords_CG.f)
  vapr.data$vapr10 <- raster::extract(vapr10, coords_CG.f)
  vapr.data$vapr11 <- raster::extract(vapr11, coords_CG.f)
  vapr.data$vapr12 <- raster::extract(vapr12, coords_CG.f)

  wind.data        <- df_CG.f 
  wind.data$wind01 <- raster::extract(wind01, coords_CG.f)
  wind.data$wind02 <- raster::extract(wind02, coords_CG.f)
  wind.data$wind03 <- raster::extract(wind03, coords_CG.f)
  wind.data$wind04 <- raster::extract(wind04, coords_CG.f)
  wind.data$wind05 <- raster::extract(wind05, coords_CG.f)
  wind.data$wind06 <- raster::extract(wind06, coords_CG.f)
  wind.data$wind07 <- raster::extract(wind07, coords_CG.f)
  wind.data$wind08 <- raster::extract(wind08, coords_CG.f)
  wind.data$wind09 <- raster::extract(wind09, coords_CG.f)
  wind.data$wind10 <- raster::extract(wind10, coords_CG.f)
  wind.data$wind11 <- raster::extract(wind11, coords_CG.f)
  wind.data$wind12 <- raster::extract(wind12, coords_CG.f)
```

```{r}
  par( mfrow=c(2,2) )
  plot  ( alt_CG.f, tmax.data$tmax07, ylim=c(0,max(tmax.data$tmax07)) )
  points( alt_CG.f, tmax.data$tmax01, col="red" )
  plot  ( alt_CG.f, prec.data$prec07, ylim=c(0,max(prec.data$prec07)) )
  points( alt_CG.f, prec.data$prec01, col="red" )
```

## Data processing

```{r}
  df_C.full <- df_C.f %>%
    mutate( Alt = alt_C.f )
  df_G.full <- df_G.f %>%
    mutate( Alt = alt_G.f )
```



\clearpage

# Introduction

This is the third progress report for project SEACAF on the process-based modelling of coffee agroforestry systems in Central America by means of the model CAF2021. The first progress report [dated 30 April 2021; @VanOijen_2021_Modelling] provided details and references on the model. The second report [dated 16 June 2021; @VanOijen_2021_Modellinga] presented changes to model structure and discussed the setup and results of a Bayesian model calibration using data from long-term experiments in Turrialba (Costa Rica) and Masatepe (Nicaragua).

Here we report on simulation of fruit production and on simulating the SEACAF farms.



\clearpage

# Reference simulations for Turrialba and Masatepe

```{r, fig.cap="\\label{fig:YieldsObsSimTM}Yields for the 32 treatments in Turrialba (black numbers) and Masatepe (red). Left: Observed yields against N-fertilisation level. Right: Observed yield vs. MAP-simulated yield."}
  source('initialisation/initialise_CAF2021_general.R')
  par( mfrow=c(1,2) )

  y <- fYieldsTM( parMatrix=parMAP, sfiles=sitesettings_filenames )
  par( pty="s" ) ; plotYieldsTM( y )
  
  # # Temporary check of setting initial tree pool values all to 0.1 kg C m-2
  # # source('initialisation/initialise_CAF2021_general.R')
  # # 
  # parMAPmod <- parMAP
  # iCtree0   <- which( startsWith( rownames(parMAPmod), "CBtree0") |
  #                     startsWith( rownames(parMAPmod), "CLtree0") |
  #                     startsWith( rownames(parMAPmod), "CRtree0") |
  #                     startsWith( rownames(parMAPmod), "CStree0") ) 
  # for(s in 1:nSites) { parMAPmod[iCtree0,] <- 0.1 }
  # ymod <- fYieldsTM( parMatrix=parMAPmod, sfiles=sitesettings_filenames )
  # par( pty="s" ) ; plotYieldsTM( ymod )

  # Temporary check of setting FWCWP to 0.2 (default is 0.4)
  # source('initialisation/initialise_CAF2021_general.R')
  # 
  parMAPmod <- parMAP
  ip   <- which( rownames(parMAPmod) == "FWCWP" ) 
  for(s in 1:nSites) { parMAPmod[ip,] <- 0.2 }
  ymod <- fYieldsTM( parMatrix=parMAPmod, sfiles=sitesettings_filenames )
  par( pty="s" ) ; plotYieldsTM( ymod )
```

We show observed vs. simulated average annual coffee dry matter yields for all 32 treatments in Fig. \ref{fig:YieldsObsSimTM}.

```{r TM, fig.height=8, fig.cap="\\label{fig:TM}Simulations for Turrialba (grey bars) and Masatepe (red)."}
  fOutTM <- fOutputTM( parMatrix=parMAP, sfiles=sitesettings_filenames )

  par( mfrow=c(6,1), mar=c(3,2,2,0) )
  
  barplotTM( fOutTM[,"harvDM_f_hay"], name="Coffee (kg DM ha-1 y-1)" )
  barplotTM( fOutTM[,"harvCPT_2"   ], name="Fruit[2] (kg DM ha-1 y-1)" )
  barplotTM( fOutTM[,"harvCST_3"   ], name="Timber[3] (kg DM ha-1 y-1)" )

  barplotTM( fOutTM[,"D_Csys" ], name="System C (kg ha-1 y-1)" )
  barplotTM( fOutTM[,"D_Csoil"], name="Soil C (kg ha-1 y-1)"   )
  barplotTM( fOutTM[,"D_Nsoil"], name="Soil N (kg ha-1 y-1)"  )
```

Below, we study the impact of adding fruit trees on various outputs from the model. The reference simulations are those that we looked at before, i.e. those for the long-term experiments in Turrialba (Costa Rica) and Masatepe (Nicaragua), which did not include any fruit trees. Model outputs for the 32 experimental treatments are shown in Fig. \ref{fig:TM}. We shall later virtually add either banana or avocado trees to the experiments and see how that changes the figure. 



\clearpage

# Banana

## Exploring parameter values for Banana

Data for coffee agroforestry farms in the Turrialba region with fruit trees were provided by Rolando Cerda (CATIE). Annual N-fertilisation levels were quantified for plots on 51 farms and ranged from 33 to 285 kg N ha-1 y-1, averaging $99 \pm 63$. On the nine plots where the only fruit trees were Musaceae, annual banana yields varied from 20 to 400 bunches ha-1 ($138 \pm 153$). These yields were not correlated with fertilisation rate, nor with the density of the trees which ranged from 30 to 1410 ha-1 ($386 \pm 424$), with the average production per tree ranging from 0.08 to 3.33 ($0.79 \pm 1.09$) bunches. The variation in these numbers is so high that we decided to calibrate banana production in CAF2021 on literature data instead, collected during the literature review reported before [@VanOijen_2021_Modelling].

- @Damour_2012_Simulation: SLA of 0.018 $m^2 g^{-1}$, light extinction coefficient = 0.7, leaf N-content 3-4% of dry matter.
- @ChavesC._2009_Modeling: plantain (Musa AAB).
  - Latin American mean yield is 7.3 t ha-1 y-1 (DM?)
  - DMP fruits ~ 25%.
  - LUE (1.63 g MJ-1)
  - critical temperatures of $T_{min}$ = 12.5 $^{\circ}$C, $T_{opt}$ = 25 $^{\circ}$C, $T_{max}$ = 40 $^{\circ}$C []
  - Allocation about equally to leaves, pseudostem and corm with during later development most going to bunches that ultimately reach up to 45% of aboveground biomass.
- @VanDenBergh_2012_Climate: critical monthly temperatures: $T_{kill}$ = 0 $^{\circ}$C, $T_{min}$ = 12 $^{\circ}$C, $T_{opt}$ = 17.5 to 26.3 $^{\circ}$C, $T_{max}$ = 33 $^{\circ}$C.
- @Dold_2007_Musa: Most common coffee agroforestry systems in the Turrialba region were coffee + *Erythrina poeppigiana* + banana/plantain + laurel (*Cordia alliodora*). Typical tree densities were 162 *E.p.* $ha^{-1}$, 179 banana/plantain $ha^{-1}$, 37 laurel $ha^{-1}$. They cite literature where poro density is 130-208 $ha^{-1}$ and banana 149-343 $ha^{-1}$ and state that banana above 120 $ha^{-1}$ would reduce coffee yield too much.
- @Dold_2010_Improving: mean tree density in central Costa Rican coffee agroforestry systems was 341 $ha^{-1}$ with 579 bananas $ha^{-1}$. In northern Nicaragua the mean tree density was 185 $ha^{-1}$ with 358 bananas $ha^{-1}$.
- @Ripoche_2012_Modeling:
  - Up to 10 kg aboveground DM per plant.
- @Jullien_2001_Withinbunch reported that pulp DMP reaches asymptotically to values of about 30%. 
- @Mustaffa_2012_Banana: leaf N content about 3% of DM.
- @MartinezAcosta_2011_Dinamica, final DM per tree, bunch / leaves / pseudostem + corm = 3000 / 1200 / 1800 g DM.
- @Schaffer_1999_Atmospheric DM of 6-month old vegetative banana (cv. 'Gros Michel'): leaves:pseudostem+rhizome:roots =  19:64:19%.
- DM-partitioning of cv. 'Williams' in Colombia not affected strongly by level of N-fertilization (0 to 483 kg N $ha^{-1}$), but fruit yields increased from 9 to 12 kg DM [@TorresB._2014_Accumulation]. At harvest after 161 kg N $ha^{-1}$ fertilization: corm+pseudostem/leaves/fruits = 6/1.5/3.5 kg DM per plant. Total plant N-concentration was 1-1.5% of DM.
- @Turner_2007_Environmental: LAI ranges from 2 to 5 m2 m-2.

## Banana simulation in CAF2021

To make CAF2021 simulate banana in a coffee plantation, we set the initial density of fruit trees (TREEDENS0(2)) to a positive value, and choose parameter settings that are appropriate for banana. We show some results in Fig. \ref{fig:SimBanana}.

```{r SimBanana, fig.height=3.5, fig.cap="\\label{fig:SimBanana}Simulating banana with CAF2021."}
  source("initialisation/initialise_CAF2021_Turrialba_19_PS_AC.R")
  pBanana <- set_par_speciesT( 2, "Banana" )
  outputB <- run_model( p=pBanana )

  par( mfrow=c(2,3), mar=c(3,3,3,3) )
  
  plot_CdistributionTrees( sim=outputB, it=2 )
  
  Time <- outputB[,1]
    i.ht2    <- which( outputNames=="h_t(2)"      ) ; h_t2      <- outputB[,i.ht2]
    i.Shade  <- which( outputNames=="Shade_f"     ) ; Shade_f   <- outputB[,i.Shade]
    i.CAt2   <- which( outputNames=="CAtree_t(2)" ) ; CAtree2   <- outputB[,i.CAt2]
    i.CPT    <- which( outputNames=="harvCPT_f"   ) ; harvCPT_f <- outputB[,i.CPT]
    YtreesDM <- harvCPT_f * 1e4 * 365 / 0.45
  plot( Time, h_t2     , type="l", ylab="", main="Height (m)" )
  plot( Time, CAtree2  , type="l", ylab="", main="Crown area (m2 tree-1)" )
  plot( Time, Shade_f  , type="l", ylab="", main="Shade (-)" )
  plot( Time, YtreesDM , type="l", ylab="", main="Fruit yield (kg DM ha-1)" )
```

We now virtually add 100 banana plants per hectare to each of the experimental treatments in Turrialba and Masatepe that we investigated above (Fig. \ref{fig:TM}). We show the *differences* from those earlier results in Fig. \ref{fig:TM.B}. 

```{r TM.B, fig.height=8, fig.cap="\\label{fig:TM.B}Differences between simulations for Turrialba (grey bars) and Masatepe (red) wtih 100 banana plants per hectare added and default simulations without fruit plants."}
  parMAP.B  <- parMAP
  for (s in 1:nSites) {
    parMAP.B[,s] <- set_par_speciesT( 2, species="Banana", p.old=parMAP[,s] )
  }
  fOutTM.B  <- fOutputTM( parMatrix=parMAP.B, sfiles=sitesettings_filenames )
  dfOutTM.B <- fOutTM.B - fOutTM

  par( mfrow=c(6,1), mar=c(3,2,2,0) )

  barplotTM( dfOutTM.B[,"harvDM_f_hay"], name="Coffee (kg DM ha-1 y-1)" )
  barplotTM( dfOutTM.B[,"harvCPT_2"   ], name="Fruit[2] (kg DM ha-1 y-1)" )
  barplotTM( dfOutTM.B[,"harvCST_3"   ], name="Timber[3] (kg DM ha-1 y-1)" )

  barplotTM( dfOutTM.B[,"D_Csys" ], name="System C (kg ha-1 y-1)" )
  barplotTM( dfOutTM.B[,"D_Csoil"], name="Soil C (kg ha-1 y-1)"   )
  barplotTM( dfOutTM.B[,"D_Nsoil"], name="Soil N (kg ha-1 y-1)"  )
```



\clearpage

# Avocado

## Exploring parameter values for Avocado

- Avocado production in Mexico is year round [@CIRAD_2019_Country]. Yield ramps up from 0.3-1.6 t ha-1 at age 4 to 12-15 t ha-1 at age 7-8 and older.
- **Elzebroek & Wind (2008)**:
  - optimal T (three races): day 20-35C, night 10-25C. [MvO: cv. Hass is on the cold side, so maybe day 25C, night 15C, 24-h optimum 20C?]
  - First harvests after 4 years (vegetatively propagated) to 5-6 yrs (seedlings)
- **http://postgrado.fausac.gt/wp-content/uploads/2019/03/Zoila-Monz%C3%B3n.pdf** (Guatemala):
  - Epocas de cosecha de aguacate (variedad Hass) en Guatemala: July-Sep & Nov-April (so 9 months in total, i.e. all months except May-June & Oct).
  - Yields in different departments from 4-11.5 t ha-1 y-1, mean 7 t ha-1 y-1.

## Avocado simulation in CAF2021

See Fig. \ref{fig:SimAvocado}.

```{r}
  source("initialisation/initialise_CAF2021_Turrialba_19_PS_AC.R")
  pAvocado <- set_par_speciesT( 2, "Avocado" )
  outputA  <- run_model( p=pAvocado )
```

```{r SimAvocado, fig.height=3.5, fig.cap="\\label{fig:SimAvocado}Simulating avocado with CAF2021."}
  par( mfrow=c(2,3), mar=c(3,3,3,3) )
  
  plot_CdistributionTrees( sim=outputA, it=2 )
  
  Time <- outputA[,1]
    i.ht2    <- which( outputNames=="h_t(2)"      ) ; h_t2      <- outputA[,i.ht2]
    i.Shade  <- which( outputNames=="Shade_f"     ) ; Shade_f   <- outputA[,i.Shade]
    i.CAt2   <- which( outputNames=="CAtree_t(2)" ) ; CAtree2   <- outputA[,i.CAt2]
    i.CPT    <- which( outputNames=="harvCPT_f"   ) ; harvCPT_f <- outputA[,i.CPT]
    YtreesDM <- harvCPT_f * 1e4 * 365 / 0.45
  plot( Time, h_t2     , type="l", ylab="", main="Height (m)" )
  plot( Time, CAtree2  , type="l", ylab="", main="Crown area (m2 tree-1)" )
  plot( Time, Shade_f  , type="l", ylab="", main="Shade (-)" )
  plot( Time, YtreesDM , type="l", ylab="", main="Fruit yield (kg DM ha-1)" )
```

We now virtually add 100 avocado trees per hectare to each of the experimental treatments in Turrialba and Masatepe. The new results are shown in Fig. \ref{fig:TM.A}, and we can compare these with the results for the simulations for the experimental conditions without fruit trees (Fig. \ref{fig:TM}).

```{r TM.A, fig.height=8, fig.cap="\\label{fig:TM.A}Differences between simulations for Turrialba (grey bars) and Masatepe (red) wtih 100 avocado trees per hectare added and default simulations without fruit trees."}
  parMAP.A  <- parMAP
  for (s in 1:nSites) {
    parMAP.A[,s] <- set_par_speciesT( 2, species="Avocado", p.old=parMAP[,s] )
  }
  fOutTM.A  <- fOutputTM( parMatrix=parMAP.A, sfiles=sitesettings_filenames )
  dfOutTM.A <- fOutTM.A - fOutTM

  par( mfrow=c(6,1), mar=c(3,2,2,0) )

  barplotTM( dfOutTM.A[,"harvDM_f_hay"], name="Coffee (kg DM ha-1 y-1)" )
  barplotTM( dfOutTM.A[,"harvCPT_2"   ], name="Fruit[2] (kg DM ha-1 y-1)" )
  barplotTM( dfOutTM.A[,"harvCST_3"   ], name="Timber[3] (kg DM ha-1 y-1)" )

  barplotTM( dfOutTM.A[,"D_Csys" ], name="System C (kg ha-1 y-1)" )
  barplotTM( dfOutTM.A[,"D_Csoil"], name="Soil C (kg ha-1 y-1)"   )
  barplotTM( dfOutTM.A[,"D_Nsoil"], name="Soil N (kg ha-1 y-1)"  )
```



\clearpage

# APPENDIX

```{r, eval=F}
  sA <- 11 ; sB <- 17 ; sC <- 31 ; sD <- 19
  source(sitesettings_filenames[sA]) ; output.MAP.A <- run_model( p=parMAP[,sA] )
  source(sitesettings_filenames[sB]) ; output.MAP.B <- run_model( p=parMAP[,sB] )
  source(sitesettings_filenames[sC]) ; output.MAP.C <- run_model( p=parMAP[,sC] )
  source(sitesettings_filenames[sD]) ; output.MAP.D <- run_model( p=parMAP[,sD] )
```

```{r, eval=F, out.width="100%", fig.cap="\\label{fig:NBalancesSoil}Soil N-balances for 4 treatments, averaged over the whole simulated period. Top row: Turrialba; bottom row: Masatepe. Simulations using the MAP parameter vector from Bayesian calibration."}
  par( mfrow=c(2,4) )

  par(mar=c(3,3,3,0))
  plot_NbalanceSoil(output.MAP.A, title1="", title2="11 TE-CM  ", ymax=800)
  par(mar=c(3,3,3,0))
  plot_NbalanceSoil(output.MAP.B, title1="", title2="17 -CI    ", ymax=800)
  par(mar=c(3,3,3,0))
  plot_NbalanceSoil(output.MAP.C, title1="", title2="31 ILSG-CM", ymax=800)
  par(mar=c(3,3,3,0))
  plot_NbalanceSoil(output.MAP.D, title1="", title2="19 -CI    ", ymax=800)
```

```{r, eval=F}
## Exploring deciduousness
  sA            <- 23 # Masatepe_05_SGTR_CI
  source(sitesettings_filenames[sA])
  params        <- parMAP[ , sA ]
  params.MAP.A  <- params
  params.MAP.A1 <- set_par( c("FTCLMINT(3)","TCLMAXT(3)"),
                            c( 0.2         , 650        ) )
  params.MAP.A2 <- set_par( c("FTCLMINT(3)","TCLMAXT(3)"),
                            c( 0.05        , 650        ) )
  params.MAP.A3 <- set_par( c("FTCLMINT(3)","TCLMAXT(3)"),
                            c( 0.2         , 365        ) )
  output.MAP.A  <- run_model( p=params.MAP.A  )
  output.MAP.A1 <- run_model( p=params.MAP.A1 )
  output.MAP.A2 <- run_model( p=params.MAP.A2 )
  output.MAP.A3 <- run_model( p=params.MAP.A3 )
  plot_output( list_output=list( output.MAP.A,
                                 output.MAP.A1, output.MAP.A2 ,output.MAP.A3),
               vars=c( "fTranT_t(3)", "LAIT_t(3)" ) )
```

```{r Balances2, eval=F, fig.height=6, fig.cap="\\label{fig:Balances2}Soil N- and C-balances at Masatepe in the ILSS_CI system. Top row: tree branches harvested and removed after pruning and thinning. Bottom row: branches left on the field as litter."}
## Comparison of leaving tree branches on the field after thinning and pruning (default) vs. removing them as harvest
  sA <- 27 # Masatepe_09_ILSS_CI
  source(sitesettings_filenames[sA])
  params        <- parMAP[ , sA ]
  params.MAP.A  <- params
  params.MAP.A1 <- set_par( c("FHARVBT(1)","FHARVBT(2)","FHARVBT(3)"),
                            c( 0          , 0          , 0          ) )
  output.MAP.A  <- run_model( p=params.MAP.A  )
  output.MAP.A1 <- run_model( p=params.MAP.A1 )
  par( mar=c(3,3,3,0), mfrow=c(2,4) )
  plot_NbalanceSoil( output.MAP.A , title1="Soil N-balance MAP", title2="" )
  par( mar=c(3,3,3,0) )
  plot_CbalanceSoil( output.MAP.A , title1="Soil C-balance MAP", title2="" )
  par( mar=c(3,3,3,0) )
  plot_NbalanceSoil( output.MAP.A1, title1="Soil N-balance 1", title2="" )
  par( mar=c(3,3,3,0) )
  plot_CbalanceSoil( output.MAP.A1, title1="Soil C-balance 1", title2="" )
```

```{r}
  # The following code chunks are for reading WorldClim (WC) data directly from R.
  # Presumably these are data from WC1.4 which we will not use here; we use WC2.1.
```

```{r}
  r_worldclim_tmean_SE <- getData('worldclim', var='tmean', res=0.5,
                              lon=-83.51, lat= 9.58)
  r_worldclim_tmean_NW <- getData('worldclim', var='tmean', res=0.5,
                              lon=-92.07, lat=15.09)
  r_worldclim_prec_SE  <- getData('worldclim', var='prec' , res=0.5,
                              lon=-83.51, lat= 9.58)
  r_worldclim_prec_NW  <- getData('worldclim', var='prec' , res=0.5,
                              lon=-92.07, lat=15.09)
  tmean_C.f <- raster::extract( r_worldclim_tmean_SE, coords_C.f )
  tmean_G.f <- raster::extract( r_worldclim_tmean_NW, coords_G.f )
  prec_C.f  <- raster::extract( r_worldclim_prec_SE , coords_C.f )
  prec_G.f  <- raster::extract( r_worldclim_prec_NW , coords_G.f )
```
    
```{r}
  #  Comparing WC2.1 with WC1.4
  par( mfrow=c(2,2) )

  plot( prec.data$prec01, c(prec_C.f[,1],prec_G.f[,1]) )
  plot( prec.data$prec07, c(prec_C.f[,7],prec_G.f[,7]) )
  plot( 0.5 * (tmin.data$tmin01 + tmax.data$tmax01),
        c(tmean_C.f[,1],tmean_G.f[,1]) )
  plot( 0.5 * (tmin.data$tmin07 + tmax.data$tmax07),
        c(tmean_C.f[,7],tmean_G.f[,7]) )
```



\clearpage

# Acknowledgements {-}

I thank the Natural Resources Institute of the University of Greenwich for funding, and my colleagues in project SEACAF and earlier projects for support.



# References {-}
